---
title: "Note to Produce ACBSP Standard 4 Items"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
    fig_height: 7
    fig_width: 7
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

Objective
================================================================================
It makes more sense to produce graphs and other items for ACBSP Standard 4 tables using the database, rather than using partial tables of `internal direct assessment` project. Hence, here it is.
Standard 4 "Fig 4.1" requires descriptions of PLOs, which are readily available in the dtabase file ("Mapping" tab). "Fig 4.2" requires outcomes of those PLOs.

- Create tables with multiple (3-5) data points, *separately* for each objective.
- As much possible, accompany them with sufficient information.

Set up
================================================================================
Data are semi-manually input from `external-direct-assessment` and `internal-direct-assessment` projects into the main Excel file. Use it as a database here.
```{r}
path <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\WIP\\"
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Main")
summary(asm)
```

The worksheet is organized in a "long" format, convenient to work with `dplyr` and `ggplot2` paradigm. If wide tables are needed, simply filter and reshape it.

```{r}
names(asm)
```

```{r}
asm %>% group_by(Program, `Assessment Type Orientation`, `Assessment Type`) %>% summarise(n = n(), n_PLO = n_distinct(`Learning Objective Number`), n_target = n_distinct(`Target Student Group`)) %>% knitr::kable()
```

```{r}
x <- asm %>% filter(Program == "Accounting",
                    `Learning Objective Number` == 1,
                    `Assessment Type Orientation` == "External",
                    `Assessment Type` == "Summative",
                    `Target Student Group` != "All")

ymin <- min(x$Outcome - 0.1, x$`Outcome Goal` - 0.1, na.rm = TRUE)
p <- ggplot(x, aes(`Academic Year`, Outcome)) +
  geom_line(na.rm = TRUE) +
  geom_point(na.rm = TRUE) +
  geom_text(aes(`Academic Year`, ymin + 0.05, label = round(`Sample Size`, 0)),
            alpha = 0.4, na.rm = TRUE) +
  geom_hline(aes(yintercept = `Outcome Goal`),
             alpha = 0.4, color = "red", na.rm = TRUE) +
  scale_y_continuous(labels=scales::percent, limits = c(ymin, 1.01))

#p + facet_wrap(vars(`Learning Objective Number`)) +
#  labs(title = title, caption = caption) +
#  theme(axis.title = element_blank(),
#        text = element_text(family = "serif"),
#        panel.grid.minor.x = element_blank(),
#        legend.position = "none")
```


