---
title: "R Notebook"
output: html_notebook
---

# Introduction

Compile the Program assessments for AY 2020.

# Data

Import data. New data are all stored in the Excel file under Internal Direct Assessment directory.

```{r}
library(tidyverse)
library(readxl)
rootpath <- "C:\\Users\\HP\\California University of Pennsylvania\\"
datapath <- paste0(rootpath, "ACBSP data reporting - Documents\\Data\\")
#
path <- paste0(datapath, "Internal Direct Assessment\\")
fn <- "Rubrics_07302021.xlsx"
rubrics <- read_xlsx(paste0(path, fn), "rubrics")
survey <- read_xlsx(paste0(path, fn), "survey")
plans <- read_xlsx(paste0(path, fn), "plans")
#
path <- datapath
fn <- "Assessment Data Main.xlsx"
sh <- c("prg", "core", "mba", "map_prg", "map_core", "map_mba")
maindf <- sapply(sh, function(x)
  read_xlsx(paste0(path, fn), sheet = x), USE.NAMES = TRUE)
```

Note that the new assessment data comes from the "Rubrics_....xlsx" while the assessment information comes from "Assessment Data Main.xlsx".
Search over the assessments (learning objectives, names, etc.) is done over the latter.

## Data Process

Clear some data issues. Note that the survey data has been manually edited to some degree.

First, simplify column names of the survey and convert types

```{r}
colnames(survey) <- c("ID", "Exclude", "Start", "Completion", "Email", "Survey Name", "Semester", "Course and Section Original", "Course and Section", "Assessment Name Original", "Assessment Name", "Rubric Grade Original", "Rubric Grade", "URL Original", "URL", "Analysis Rubric", "Action Rubric", "LO", "n", "s", "Analysis Non Rubric", "Action Non Rubric")
colnames(survey) <- make.names(colnames(survey))
survey <- survey %>% mutate(across(c(n, s), as.numeric))

# Extract ID's from URL
x <- str_match(survey$URL, "(rubricId\\=)(\\d+)")[, 3]
y <- str_match(survey$URL, "(ou\\=)(\\d+)")[, 3]
survey <- bind_cols(survey, RubricId = as.numeric(x), ou = as.numeric(y))
# Split course and section
survey <- survey %>% mutate(
  Course = paste(str_sub(Course.and.Section, 1, 3),
                 str_sub(Course.and.Section, 4, 6)),
  Section = str_sub(Course.and.Section, 8, 10))

# Split survey
survey.r <- survey %>% filter(Rubric.Grade == "Yes")
survey.n <- survey %>% filter(Rubric.Grade == "No")
# Record course IDs
clevels.r <- levels(factor(survey.r$Course))
clevels.n <- levels(factor(survey.n$Course))
```

Likewise, rubrics. There's some special character in one of columns.

```{r}
names(rubrics) <- make.names(names(rubrics))
names(rubrics)[2] <- "AssessmentId"
names(rubrics)[4] <- "Score"
names(rubrics)[11] <- "Criteria"
names(rubrics)[15] <- "Level"
```

Next, clean up the level achieved in the rubric data.

```{r}
patterns <- c(
  "Unsatisactory" = "Unsatisfactory",
  "Unsatisfactory" = "Unacceptable",
  "Advaned" = "Excellent",
  "Advanced" = "Excellent",
  "Proficient" = "Good",
  "Devloping" = "Basic",
  "Developing" = "Basic",
  "Fair" = "Basic",
  "Emerging" = "Rudimentary"
)
clean_levels <- function(x, patterns){
  z <- str_replace_all(x, "[^a-zA-Z\\s]+", "")
  z <- str_trim(z)
  z <- str_replace_all(z, patterns)
  z
}
rubrics <- rubrics %>% mutate(LevelAchieved = clean_levels(Level, patterns))

# Met
rubrics <- rubrics %>% mutate(
  Met.UND = case_when(
    is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" | LevelAchieved == "Basic" ~ "Met",
    LevelAchieved == "Rudimentary" | LevelAchieved == "Unacceptable" ~ "Not",
    TRUE ~ "Other"),
  Met.GRD = case_when(
    is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" ~ "Met",
    LevelAchieved == "Basic" | LevelAchieved == "Rudimentary" | LevelAchieved == "Unacceptable" ~ "Not",
    TRUE ~ "Other"),
  
  )
```

Then, combine the two for further processes.

```{r}
rubrics.orig <- rubrics
rubrics <- rubrics.orig # Prevent iterative proc
rubrics <- left_join(rubrics, survey.r, by = "RubricId", suffix = c(".rub", ".suv"))
# Split into achievements and misc like attributes
rubrics.a <- rubrics %>% filter(str_detect(Criteria, "Major|Minor|Certificate|Specialization|MBA|New Criterion|Sorting values|Diplomacy certificate", negate = TRUE))
rubrics.m <- rubrics %>% filter(str_detect(Criteria, "Major|Minor|Certificate|Specialization|MBA|New Criterion|Sorting values|Diplomacy certificate", negate = FALSE))
```

Lastly, define some misc variables.

```{r}
# Define misc
clevels.plan <- levels(factor(plans$Course))
```

## Data Notes

Some standardization is needed, although some of them may not be worthwhile at the moment. The department will be split into different groups.
In order to make the assessment for 2021-22 easy, I shall focus on the primary concerns. List them with solutions.

- Signature Assignment names: Drop menu in survey
- Level Achieved: No action. Use the rubrics posted.
- 

# Core Assessment

See Note 3 for the Business Core assessment with disaggregation by majors.

# Program Assessment

There are exam/score based assessments and rubric-based assessments by design. There may be some assessments that have both "by accident" (e.g., some faculty members didn't follow the direction). Ignore the latter case for now.

## Check by Rubric

Program learning objectives (PLOs) are stored in the database. Filter the PLOs that use rubrics.

This PLO list contains the relevant information including the identifiers to pick up relevant assessment outcomes.

```{r}
plolist <- maindf$map_prg %>% filter(group1 == "Course", internal_rubric_keys2020 != "No Rubric")
plolist

plolist <- bind_rows(plolist, maindf$map_prg %>% filter(plo_id == "FIN 1-Summative-Internal"))
plolist <- bind_rows(plolist, maindf$map_prg %>% filter(plo_id == "FIN 2-Summative-Internal"))
```

Using this list, identify the observations and check them for errors.

- Loop through rows
- Keep the summary stats
- Have an easy access to review the data (Easier to do with object... Later?)


```{r}
get_outcome <- function(i, dict = plolist, out = rubrics.a){
  # From the row number, extract relevant assessment outcomes
  x <- dict[i, ]
  # Obtain a summary of the assessment
  mdf <- out %>% filter(Course == x$group2, Assessment.Name == x$tool) %>% 
    filter(str_detect(Criteria,
                      regex(x$internal_rubric_keys2020, ignore_case = TRUE)))
  res <- mdf %>% summarise(
    plo = x$plo,
    main_n = n_distinct(UserId),
    main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
  res
}

```

Since I cannot use the same naming method as Core (where it only had BUS), use the PLO from the dictionary. Then, it's ready to be combined by rows. (Also, unlike BUS, there is no need to widen the data.)

```{r}
lout <- lapply(1:nrow(plolist), get_outcome)
xx <- bind_rows(lout)
xx
```

Names are mostly corrected in Note 3.

A remaining major issue is from MKT 401, where the names vary within each section and across sections. Moreover, the description in the OneNote differs from what is stated in the survey and contains no rubric. >> Follow up with Rich and Al.

In addition, FIN 302 Capital Budgeting needs some clarification. >> Follow up with Chris and Nan.

Export the data for Nuventive reporting.

```{r}
write_csv(xx, "out/prg_internal.csv")
```


## Check by Non-Rubric

```{r}
survey.n
```

```{r}
plolist <- maindf$map_prg %>% filter(group1 == "Course", internal_rubric_keys2020 == "No Rubric")
plolist

```
 Check manually.
 
```{r}
survey.n %>% filter(Course == "ACC 331")
survey.n %>% filter(Course == "ACC 318")
survey.n %>% filter(Course == "ECO 301")
survey.n %>% filter(Course == "ECO 302")
survey.n %>% filter(Course == "FIN 302")
survey.n %>% filter(Course == "MIS 401")
```


- ACC 331. Only one is reported. "calculate product/period costs using multiple costing methods". Is that ACC 2?
- ECO 302 is missing. Not offered?
- FIN 302 reported with rubric. Needs update in the database. (How do I keep track of the change over time??)
- MIS 401. Confirmed. Use for MIS 2.

Now, manually append the generated file for reporting.

```{r}
survey.n %>% group_by(Course) %>% summarise(n = sum(n), s = sum(s)) %>% mutate(Met = s/n)
```

# MAcc Assessment

Apparently, MAcc Internal Assessment is done as well. (No discussions as far as I can tell from my meeting notes.)

```{r}
x <- rubrics.a %>% filter(Course == "ACC 735")
levels(factor(x$Assessment.Name))
# "Final Whitepaper"
levels(factor(x$LevelAchieved))
levels(factor(x$Met.GRD))
levels(factor(x$Score))
# Useless achievement level data. Sum the score instead.

x <- rubrics.a %>% filter(Course == "ACC 710")
levels(factor(x$Assessment.Name))
# "Financial Accounting Research Project"
levels(factor(x$LevelAchieved))
# "Basic" "Excellent" "Good"
levels(factor(x$Met.GRD))
levels(factor(x$Score))
```

```{r}
x <- rubrics.a %>% filter(Course == "ACC 735")
scores <- x %>% group_by(UserId, Assessment.Name) %>%
  summarise(Score = sum(Score)) %>%
  mutate(Met.GRD = case_when(
    is.na(Score) ~ "Missing",
    Score >= 85 ~ "Met",
    Score < 85 ~ "Not",
    TRUE ~ "Other"))

res1 <- scores %>% ungroup() %>% 
  summarise(
    plo = "MACC 1",
    main_n = n_distinct(UserId),
    main_outcome = mean((Met.GRD == "Met"), na.rm = TRUE))

res1
```



```{r}
mdf <- rubrics.a %>%
  filter(Course == "ACC 710",
         Assessment.Name == "Financial Accounting Research Project")

res2 <- mdf %>% summarise(
  plo = "MACC 2",
  main_n = n_distinct(UserId),
  main_outcome = mean((Met.GRD == "Met"), na.rm = TRUE))
```

```{r}
xx <- bind_rows(list(res1, res2))
write_csv(xx, "out/macc_internal.csv")
```


# IGB Program

Apparently Integrated Global Business is assessed as well. Now I found Ed updated his Excel file in the shared folder. Use BUS 345.

Prepare for attributes. Hopefully, it's not as messy as BUS 499.

```{r}
att <- rubrics.m %>%
  filter(Course == "BUS 345") %>% select(UserId, Criteria, Level, Course.and.Section) %>%
  filter(str_detect(Criteria,
                    regex("Major", ignore_case = TRUE)))

levels(factor(att$Level))
levels(factor(att$Criteria))
```

Test some replacements
```{r}
x <- levels(factor(att$Level))
x

str_replace_all(x, "Non-(B|b)usiness.*", "Other")
str_replace_all(x, "Other (B|b)usiness.*", "General Business") # Econ?
str_replace_all(x, "Excellent|Rudimentary|Unacceptable", "Error") # Econ?


mdf <- att %>% rename(Major = Level)
sdf <- mdf %>% mutate(
  Major = str_replace_all(Major, "Non-(B|b)usiness.*", "Other"),
  Major = str_replace_all(Major, "Integrated Global Business", "IGB"),
  Major = str_replace_all(Major, "Other (B|b)usiness.*", "General Business"),
  Major = str_replace_all(Major, "Excellent|Rudimentary|Unacceptable", "Error")
)

levels(factor(sdf$Major))
```

```{r}
names(sdf)

head(sdf)

sdf %>% summarise(n_distinct(UserId, Course.and.Section))
```
```{r}
mdf <- left_join(rubrics.a %>% filter(Course == "BUS 345"),
               sdf %>% select(-Criteria),
               by = c("UserId", "Course.and.Section"))

names(mdf)
```

```{r}
lres <- list()
```


First CLO.

```{r}
sdf <- mdf %>%
  filter(Course == "BUS 345", Assessment.Name == "Ethics Final Paper") %>% 
  filter(str_detect(Criteria,
                    regex("Plo1", ignore_case = TRUE)))

lres[["IGB1"]] <- sdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE)) %>% 
  mutate(PLO = "LGB1")
```

```{r}
sdf <- mdf %>%
  filter(Course == "BUS 345", Assessment.Name == "Ethics Final Paper") %>% 
  filter(str_detect(Criteria,
                    regex("Plo5", ignore_case = TRUE)))

lres[["IGB2"]] <- sdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE)) %>% 
  mutate(PLO = "LGB2")
```

```{r}
sdf <- mdf %>%
  filter(Course == "BUS 345", Assessment.Name == "Ethics Final Paper") %>% 
  filter(str_detect(Criteria,
                    regex("Plo7", ignore_case = TRUE)))

lres[["IGB3"]] <- sdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE)) %>% 
  mutate(PLO = "LGB3")
```
```{r}
sdf <- mdf %>%
  filter(Course == "BUS 345", Assessment.Name == "Ethics Reflection") %>% 
  filter(str_detect(Criteria,
                    regex(".*", ignore_case = TRUE)))

lres[["IGB4"]] <- sdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE)) %>% 
  mutate(PLO = "LGB4")
```

```{r}
xx <- bind_rows(lres)

output <- pivot_wider(xx, id_cols = PLO, names_from = Major, values_from = c(main_outcome, main_n))
```

```{r}
output
write_csv(output, "out/igb_internal.csv")
```

# Marketing

```{r}
xx <- rubrics.a %>% filter(Course == "MKT 401")
levels(factor(xx$Name))
```
```{r}
levels(factor(xx$Assessment.Name))
```
```{r}
sig1 <- xx %>% filter(Assessment.Name== "Strategic Plan")
sig2 <- xx %>% filter(Assessment.Name== "Management Audit")
sig3 <- xx %>% filter(Assessment.Name== "Advertising Story Board")
```

```{r}
table(sig1$Criteria, sig1$Semester)
```


```{r}
table(sig2$Criteria, sig2$Semester)
```

```{r}
table(sig3$Criteria, sig3$Semester)
```

It's gonna be a paint to reconcile summer and spring for Sig 1. Perhaps I can skip for now.

Many learning objectives are still there. PLOs are spread across assignments. I want a proper documentation for this. Again, simplify as needed for now.

How can I handle this? Merge the assignments into one. Aggregate by student. (Number would vary due to missing submissions though.)


```{r}
sig <- xx %>% filter(Assessment.Name %in% c("Strategic Plan", "Management Audit", "Advertising Story Board"))
```



```{r}
plo1 <- sig %>% filter(str_detect(Criteria, "PLO 1"))
levels(factor(plo1$Criteria))
plo1 <- plo1 %>% summarise(Met = mean(Met.UND == "Met"), n = n_distinct(UserId))
```
```{r}
plo2 <- sig %>% filter(str_detect(Criteria, "PLO 2"))
levels(factor(plo2$Criteria))
plo2 <- plo2 %>% summarise(Met = mean(Met.UND == "Met"), n = n_distinct(UserId))
```


```{r}
plo3 <- sig %>% filter(str_detect(Criteria, "PLO 3"))
levels(factor(plo3$Criteria))
```
```{r}
plo4 <- sig %>% filter(str_detect(Criteria, "PLO 4"))
levels(factor(plo4$Criteria))
```
```{r}
plo5 <- sig %>% filter(str_detect(Criteria, "PLO 5"))
levels(factor(plo5$Criteria))
plo5 <- plo5 %>% summarise(Met = mean(Met.UND == "Met"), n = n_distinct(UserId))
plo5
```

```{r}
plo6 <- sig %>% filter(str_detect(Criteria, "PLO6"))
levels(factor(plo6$Criteria))
plo6 <- plo6 %>% summarise(Met = mean(Met.UND == "Met"), n = n_distinct(UserId))
plo6
```

```{r}
plo7 <- sig %>% filter(str_detect(Criteria, "PLO7"))
levels(factor(plo7$Criteria))
```

```{r}
plo8 <- sig %>% filter(str_detect(Criteria, "PLO 8"))
levels(factor(plo8$Criteria))
```

```{r}
plo9 <- sig %>% filter(str_detect(Criteria, "PLO 9"))
levels(factor(plo9$Criteria))
plo9 <- plo9 %>% summarise(Met = mean(Met.UND == "Met"), n = n_distinct(UserId))
plo9
```

```{r}
res <- bind_rows(plo1, plo2, plo5, plo6, plo9)
write_csv(res, "out/mkt_internal.csv")
```

# FIN

Chris passed the data to Ed directly. It's efficient, given that he was the only one having taught that class. I'll still need to sort out the rubrics though.



