---
title: "Note to Incorporate Disaggregate Data 01"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
    fig_height: 7
    fig_width: 7
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
```

Introduction
================================================================================

Objective
--------------------------------------------------------------------------------
For Business Core, I'd like to incorporate the information dissaggregated by students' majors.
However, because I used the aggregate data for this project, I don't have an immediate access to such analyses from internal and external assessment projects. Let's incorporate them here.

Data
--------------------------------------------------------------------------------
What data I need depends on the code I have in those projects. Simply keep notes here and explore linearly in the following sections.

Explore
================================================================================

Internal Assessment
--------------------------------------------------------------------------------
From `note_inspecting_rubric_data08.Rmd`, retrieve some code.

```
attr <- mdf %>% filter(str_detect(Name, "Major|Minor")) %>% 
  select(RubricId, UserId, Course, Assessment, Name, LevelAchieved.Original)
attr.unq <- attr %>% distinct()

majors <- attr.unq %>% filter(Name == "Major")
majors.buscore <- majors %>% filter(Course == "BUS 499")
pttrn.major <- c("General Busines{1,3}" = "General Business",
                 "Integrated Global Business.*" = "Integrated Global Business")
majors.buscore <- majors.buscore %>%
  mutate(Major = str_to_title(LevelAchieved.Original),
         Major = str_replace_all(Major, pttrn.major))
table(majors.buscore$Major)
head(majors.buscore)
# Merge
sdf <- mdf %>% filter(Course == "BUS 499") %>% left_join(majors.buscore %>% select(RubricId, UserId, Major), by = c("RubricId", "UserId"))

res <- sdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Assessment, Name, PLO, Major) %>%
  summarise(Met.UND = mean(Met.UND.bin), Met.GRD = mean(Met.GRD.bin),
            n = n_distinct(UserId))
```

> `mdf` or main data frame contains the rubric outcome data merged with the course/assessment information gathered from the survey. Data are cleaned up.

Copy the scripts from the project, modify the source directories, and skip duplicate datasets:
```{r}
source('int_read.R')
source('int_munge.R')
```

Then, use the existing code.

- First, extract observations about students' majors and minors.
- For simplicity, focus on majors this time. Also, focus on business core (BUS 499).
- Clean up the data.
- Merge the data on majors into the rubric outcomes

```{r}
attr <- mdf %>% filter(str_detect(Name, "Major|Minor")) %>% 
  select(RubricId, UserId, Course, Assessment, Name, LevelAchieved.Original)
attr.unq <- attr %>% distinct()
# dim(attr); dim(attr.unq)

majors <- attr.unq %>% filter(Name == "Major")
majors.buscore <- majors %>% filter(Course == "BUS 499")

pttrn.major <- c("General Busines{1,3}" = "ISBC",
                 "Interdisciplinary Studies In Business And Commerce" = "ISBC",
                 "Integrated Global Business.*" = "Integrated Global Business")
majors.buscore <- majors.buscore %>%
  mutate(Major = str_to_title(LevelAchieved.Original),
         Major = str_replace_all(Major, pttrn.major))
# table(majors.buscore$Major)
# head(majors.buscore)
sdf <- mdf %>% filter(Course == "BUS 499") %>%
  left_join(majors.buscore %>% select(RubricId, UserId, Major),
            by = c("RubricId", "UserId"))
```


```{r}
res <- sdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Assessment, Name, PLO, Major) %>%
  summarise(Met.UND = mean(Met.UND.bin), Met.GRD = mean(Met.GRD.bin),
            n = n_distinct(UserId))
knitr::kable(res, dig = 2)
```

Map them into PLOs. Brute force.
```{r}
lres <- list()
lres[["PLO2"]] <- res %>% filter(str_detect(Name, "Plo2")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 2)
lres[["PLO3"]] <- res %>% filter(str_detect(Name, "Plo3")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 3)
lres[["PLO4"]] <- res %>% filter(str_detect(Name, "Plo4")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 4)
lres[["PLO5"]] <- res %>% filter(str_detect(Name, "5[a|b|c|d]")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 5)
lres[["PLO6"]] <- res %>% filter(str_detect(Name, "6[e|f|g]")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 6)
lres[["PLO7"]] <- res %>% filter(str_detect(Name, "Plo7")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 7)
lres[["PLO8"]] <- res %>% filter(str_detect(Name, "Plo8")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 8)
lres[["PLO9"]] <- res %>% filter(str_detect(Name, "Plo9")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 9)
lres[["PLO10"]] <- res %>% filter(str_detect(Name, ".*")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 10)

out <- bind_rows(lres)
knitr::kable(out, dig=2)
```
```{r}
p <- ggplot(out %>% filter(PLO == 2), aes(str_sub(Major, 1, 15), Met - 0.7))
p + geom_col(width = 0.05) + geom_point() +  coord_flip()
```


```{r}
p <- ggplot(out %>% filter(Major == "Management"),
            aes(factor(PLO), Met - 0.7))
p + geom_col()
```

External Assessment
--------------------------------------------------------------------------------
Reviewing the criteria, realized that Peregrine test scores are already "disaggregated" in each program's external assessments. Perhaps I can show the scores for each topic broken down by majors... but Ahmet should be working on those. Let's skip for now.

