---
title: "Note 01 for annual reports"
date: "11/22/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
datapath <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
```

# Objectives

For the Middle State requirements (*Quality Assurance Report*), we need to have our outcome posted on our school website (https://www.calu.edu/academics/business/learning-outcomes/index.aspx).
They don't have to be through and can cherry-pick to some degree. I'd like to make a mock up and check, then make those for all the programs.

This is also a good chance to go over the outcomes/findings before the conference presentaiton.


# Plan

First, I'd like to make sure I have all the data visualizations. At the moment of writing, there seems to be some issues with internal direct assessments.
Then, I will make a minimal example to share with others. I only have a couple of days, so this is likely outcomes.
Finally, if time allows, I'd like to make more condense version similar to the style of conference posters.

I need to have some scripts:
- Rubric data to internal assessment
- Peregrine data to external assessment
- Retrieval of existing assessment outcomes


# Data Visualization

Notes are all over the place and hard to keep track of them.
As a solution, I created an index file that will link to all the notes with descriptions.

All the visualizations are derived from the up-to-date database, incorporating the past assessment results and the latest outcomes.
For data generation of the latest outcome, refer to the following:
- `note_update_ext_direct_02.Rmd`

```{r load}
program <- read_excel(paste0(datapath, "Assessment Data Main.xlsx"), "Program")
core <- read_excel(paste0(datapath, "Assessment Data Main.xlsx"), "Core1")
asm_map <- read_excel(paste0(datapath, "Assessment Data Main.xlsx"), "Mapping")
```

```{r}
draw_time <- function(lo, ori, typ, stgrp,
                      ay = "ay", compare = FALSE, use_core = FALSE){
  # Given the data import: program, core, asm_map
  # Specify column names (mostly internal vs external)
  ay <- "ay"
  if(ori == "External"){
    outcome <- "external_outcome"
    goal <- "external_goal"
    grp <- "external_group"
    des <- "external_tool_description"
  }else{
    outcome <- "internal_outcome"
    goal <- "internal_goal"
    grp <- "internal_group"
    des <- "internal_tool_description"
  }
  # Select data and mapping
  if(use_core){
    x <- core %>% filter(plo == lo, type == typ, .data[[grp]] == stgrp)
  }else{
    x <- program %>% filter(plo == lo, type == typ, .data[[grp]] == stgrp)
  }
  y <- asm_map %>% filter(plo == lo, type == typ)
  
  # Create titles
  tool <- asm_map %>% filter(plo == lo) %>% pull(des)
  ttl <- paste(lo, ori, typ)
  subt <- paste0("Assessment Tool: ", str_trunc(tool, 50, "right"))
  # Base plot
  p <- ggplot(x, aes_string(ay, outcome)) +
    geom_hline(data = y, aes_string(yintercept = goal),
               alpha = 0.4, color = "red", na.rm = TRUE)
  if(compare){
    p <- p +
      geom_line(aes_string(group = grp, linetype = grp), na.rm = TRUE) +
      geom_point(aes_string(group = grp, shape = grp), size = 2, na.rm = TRUE) +
      scale_shape_manual(values = c(16, 1), labels = c("Focus", "All Business")) +
      scale_linetype(labels = c("Focus", "All Business")) +
      scale_y_continuous(labels=scales::percent_format(accuracy = 5L))
    # Update subtitle
    subt <- paste0(subt, "\nFocus Group: ", stgrp)
  } else{
    # Add data (No comparison)
    p <- p + geom_line(aes_string(), na.rm = TRUE) +
      geom_point(aes_string(), size = 2, na.rm = TRUE) +
      scale_y_continuous(labels=scales::percent_format(accuracy = 5L))
  }
  # Decorate
  p <- p +
    labs(title = ttl, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    ggthemes::theme_fivethirtyeight(base_size = 7) +
    theme(legend.position = "right", legend.direction = "vertical")
  
  # print(paste(lo, ori, typ, stgrp))
  # print(paste(outcome, goal, grp))
  # return(list(x, y, p))
  p
}

draw_time(lo = "ACC 1", ori = "External", typ = "Summative", stgrp = "Accounting")
draw_time(lo = "BUS 1", ori = "External", typ = "Summative", stgrp = "All", use_core = TRUE)
draw_time(lo = "BUS 1", ori = "External", typ = "Summative", stgrp = "Accounting", use_core = TRUE)
draw_time(lo = "ACC 1", ori = "Internal", typ = "Summative", stgrp = "Course")
```


```{r}
dir.create("out")
dir.create("out/und_core/")
# test <- draw_time(lo = "ACC 1", ori = "External", typ = "Summative", stgrp = "Accounting Major")
# ggsave("fig/und_core/test.png", test,
#        height = 2, width = 3.5, units = "in")
```

```{r}
dir.create("out/und_prog/")
for(i in 1:nrow(asm_map)){
  x <- asm_map[i, ]
  p <- draw_time(lo = x$plo, ori = "Internal", typ = x$type, stgrp = x$internal_group)
  # print(p)
  fn <- paste0("out/und_prog/", x$plo, "_int_", x$type, ".png")
  print(paste("Save ", fn, "..."))
  ggsave(fn, p,
         height = 2, width = 3.5, units = "in")
}
```

```{r}
for(i in 1:nrow(asm_map)){
  x <- asm_map[i, ]
  p <- draw_time(lo = x$plo, ori = "External", typ = x$type, stgrp = x$external_group)
  # print(p)
  fn <- paste0("out/und_prog/", x$plo, "_ext_", x$type, ".png")
  print(paste("Save ", fn, "..."))
  ggsave(fn, p,
         height = 2, width = 3.5, units = "in")
}
```

```{r}
dir.create("out/und_core/")

m <- filter(asm_map, core)

for(i in 1:nrow(m)){
  x <- m[i, ]
  p <- draw_time(lo = x$plo, ori = "External", typ = x$type, stgrp = "All", use_core = TRUE)
  # print(p)
  fn <- paste0("out/und_core/", x$plo, "_ext_", x$type, ".png")
  cat(paste("Save ", fn, "..."))
  ggsave(fn, p,
         height = 2, width = 3.5, units = "in")
}
for(i in 1:nrow(m)){
  x <- m[i, ]
  p <- draw_time(lo = x$plo, ori = "Internal", typ = x$type, stgrp = "All", use_core = TRUE)
  # print(p)
  fn <- paste0("out/und_core/", x$plo, "_int_", x$type, ".png")
  cat(paste("Save ", fn, "..."))
  ggsave(fn, p,
         height = 2, width = 3.5, units = "in")
}
```


# Closing

The note served its purpose. The annual reports are compiled manually, using the graphs produced here. Finalize this note.

Next, update the database Excel file and re-create the outcomes here. Produce more elaborate version of annual reports. Also, start planning for formative assessments.

