---
title: "Note 01 for annual reports"
date: "11/24/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
datapath <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
```

# Objectives

For the Middle State requirements (*Quality Assurance Report*), we need to have our outcome posted on our school website (https://www.calu.edu/academics/business/learning-outcomes/index.aspx).
They don't have to be thorough and can cherry-pick to some degree. I'd like to make a mock up and check, then make those for all the programs.

In this note, I test a different configuration of the data file.


# New Database Layout

Now the data are stored in separate worksheets. Load them all.

```{r load}
sns <- c("prg", "core", "mba")
mns <- paste0("map_", sns)

# strsplit("program	plo	type	source	ay	group	n	outcome", "\t")[[1]]

ldf <- sapply(sns, function(x) read_excel(paste0(datapath, "Assessment Data Main.xlsx"), x), simplify = FALSE, USE.NAMES = TRUE)
lmp <- sapply(mns, function(x) read_excel(paste0(datapath, "Assessment Data Main.xlsx"), x), simplify = FALSE, USE.NAMES = TRUE)
```

With the data set split into worksheets, it's straightforward to make graphs.

```{r}
ggplot(ldf$prg %>% filter(source == "Internal"), aes(ay, outcome, group = plo)) + geom_line()
```

It is easy to manipulate them.

```{r}
ldf$prg %>% pivot_wider(names_from = source, values_from = c(n, outcome))
```

## Recreate

Now, recreate some visualizations.

First element in the mapping:

```{r}
x <- lmp$map_prg[1, ]

p <- ldf$prg %>% filter(plo == x$plo, type == x$type, source == x$source) %>% 
  ggplot(aes(ay, outcome)) + geom_line(na.rm = TRUE) +
  geom_hline(aes(yintercept = x$target), alpha = 0.4, color = "red") +
  geom_point(size = 2, na.rm = TRUE)

p <- p + scale_y_continuous(labels=scales::percent_format(accuracy = 5L))


# tool <- asm_map %>% filter(plo == lo) %>% pull(des)
ttl <- paste(x$plo, x$type, x$source)
subt <- paste0("Assessment Tool: ", x$tool)
p +
  labs(title = ttl, subtitle = subt) +
  xlab("Academic Year\nSample Size") +
  ggthemes::theme_fivethirtyeight(base_size = 7) +
  theme(legend.position = "right", legend.direction = "vertical")
```

ACC1 again but external:

```{r}
x <- lmp$map_prg %>% filter(plo == "ACC 1", source == "External")
x

p <- ldf$prg %>% filter(plo == x$plo, type == x$type, source == x$source) %>% 
  ggplot(aes(ay, outcome)) + geom_line(na.rm = TRUE) +
  geom_hline(aes(yintercept = x$target), alpha = 0.4, color = "red") +
  geom_point(size = 2, na.rm = TRUE)

p <- p + scale_y_continuous(labels=scales::percent_format(accuracy = 5L))


# tool <- asm_map %>% filter(plo == lo) %>% pull(des)
ttl <- paste(x$plo, x$type, x$source)
subt <- paste0("Assessment Tool: ", x$tool)
p +
  labs(title = ttl, subtitle = subt) +
  xlab("Academic Year\nSample Size") +
  ggthemes::theme_fivethirtyeight(base_size = 7) +
  theme(legend.position = "right", legend.direction = "vertical")
```

Comparison group data are missing, though. What organization would make sense?
This is the database I draw information from. Robustness over flexibility. Store the reference as recorded in the mapping. (Task for external assessment script)

## Process Internal Assessment

### Prepare

Using the new mapping files, process the internal assessments.
Get codes from `note_inspecting_rubric_data08.Rmd` in `internal-direct` project.

```{r}
source('R/int_read.R')
source('R/int_munge.R')
# User level data
names(mdf)
head(mdf)

# 1. Summarize to section, semester level
# 2. Merge with non-rubric data
# 3. Summarize to course level

tbl1 <- mdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Course, Section, Semester, Assessment, Name, PLO) %>%
  summarise(Met.UND = mean(Met.UND.bin), Met.GRD = mean(Met.GRD.bin),
            n = n_distinct(UserId),
            Rubric = TRUE)
miss <- read_excel(paste0(path, "D2L Missing Data Retrievals.xlsx"), "Scraped")
miss <- miss %>% mutate(Rubric = FALSE) %>% 
  select(-c(Unsatisfactory:Advanced)) %>% mutate(Met.UND = Met, Met.GRD = Met)
tbl2 <- bind_rows(tbl1, miss)
tbl3 <- tbl2 %>%
  bind_rows(non %>% transmute(Course, Section, Semester, Assessment,
                              Name = "No Rubric", PLO,
                              Met.UND = np/n, Met.GRD = Met.UND, n,
                              Rubric = FALSE))
tbl4 <- tbl3 %>% 
  group_by(Course, Assessment, Name, PLO, Rubric) %>%
  summarise(Met.UND = weighted.mean(Met.UND, n, na.rm = TRUE),
            Met.GRD = weighted.mean(Met.GRD, n, na.rm = TRUE),
            n = sum(n, na.rm = TRUE), n.sec = n_distinct(Section)
            ) %>% 
  ungroup()
```

The same notebook extracts relevant rows from `tbl4`, but the rest of that notebook is rather complicated for no good reason. Time to simplify it.
It will be useful when I revisit formative assessments later.

The data `tbl4` contains `Course-Semester-Assessment-RubricRaw(Name)` data.
Need to further aggregate for certain assessment criteria.

```{r}
table(tbl4$PLO)
table(tbl4$Rubric)
```

### Select Program

Use the keys in the mapping.

```{r}
# map1 <- lmp$map_prg %>% filter(source == "Internal")
map1 <- lmp$map_prg %>% filter(group1 == "Course")

tbl5 <- tbl4 %>% filter(PLO %in% map1$internal_rubric_tags)
```


```{r}
lres <- list()
for(i in 1:nrow(map1)){
  x <- map1[i, ]
  lres[[i]] <- tbl5 %>%
    filter(PLO == x$internal_rubric_tags,
           str_detect(Name, x$internal_rubric_keys2019)) %>% 
    mutate(plo = x$plo)
}


# Summarized for PLOs
tbl_assess <- bind_rows(lres) %>%
  group_by(plo) %>%
  summarize(Met = mean(Met.UND), n = max(n))
```

```{r}
write_csv(tbl_assess, "out/prg_internal.csv")
```

### Select Core

Likewise, filter out from `tbl4`

```{r}
map1c <- lmp$map_core %>% filter(group1 == "Course")

tbl5c <- tbl4 %>% filter(PLO %in% map1c$internal_rubric_tags)
```

```{r}
lres <- list()
for(i in 1:nrow(map1c)){
  x <- map1c[i, ]
  lres[[i]] <- tbl5c %>%
    filter(PLO == x$internal_rubric_tags,
           str_detect(Name, x$internal_rubric_keys2019)) %>% 
    mutate(plo = x$plo)
}

# Summarized for PLOs
tbl_assess <- bind_rows(lres) %>%
  group_by(plo) %>%
  summarize(Met = mean(Met.UND), n = max(n))
```

But also want a disaggregation of the scores.
Brute force. From `int_prepare.R`

```{r}
attr <- mdf %>% filter(str_detect(Name, "Major|Minor")) %>% 
  select(RubricId, UserId, Course, Assessment, Name, LevelAchieved.Original)
attr.unq <- attr %>% distinct()
# dim(attr); dim(attr.unq)

majors <- attr.unq %>% filter(Name == "Major")
majors.buscore <- majors %>% filter(Course == "BUS 499")

pttrn.major <- c("General Busines{1,3}" = "ISBC",
                 "Interdisciplinary Studies In Business And Commerce" = "ISBC",
                 "Integrated Global Business.*" = "ISBC")
majors.buscore <- majors.buscore %>%
  mutate(Major = str_to_title(LevelAchieved.Original),
         Major = str_replace_all(Major, pttrn.major))
# table(majors.buscore$Major)
# head(majors.buscore)
sdf <- mdf %>% filter(Course == "BUS 499") %>%
  left_join(majors.buscore %>% select(RubricId, UserId, Major),
            by = c("RubricId", "UserId"))

res <- sdf %>% filter(str_detect(Name, "Major|Minor", negate = TRUE)) %>%
  group_by(Assessment, Name, PLO, Major) %>%
  summarise(Met.UND = mean(Met.UND.bin), Met.GRD = mean(Met.GRD.bin),
            n = n_distinct(UserId))
lres <- list()
lres[["PLO2"]] <- res %>% filter(str_detect(Name, "Plo2")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 2)
lres[["PLO3"]] <- res %>% filter(str_detect(Name, "Plo3")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 3)
lres[["PLO4"]] <- res %>% filter(str_detect(Name, "Plo4")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 4)
lres[["PLO5"]] <- res %>% filter(str_detect(Name, "5[a|b|c|d]")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 5)
lres[["PLO6"]] <- res %>% filter(str_detect(Name, "6[e|f|g]")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 6)
lres[["PLO7"]] <- res %>% filter(str_detect(Name, "Plo7")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 7)
lres[["PLO8"]] <- res %>% filter(str_detect(Name, "Plo8")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 8)
lres[["PLO9"]] <- res %>% filter(str_detect(Name, "Plo9")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 9)
lres[["PLO10"]] <- res %>% filter(str_detect(Name, ".*")) %>% group_by(Major) %>% summarise(Met = mean(Met.UND), n = min(n)) %>% mutate(PLO = 10)
out <- bind_rows(lres)

out_wide <- pivot_wider(out, id_cols = PLO, names_from = Major, values_from = c(Met, n))
```

```{r}
write_csv(out_wide, "out/core_internal.csv")
```

## Process External Assessment

### Prepare

Import individual data and benchmark scores.
```{r}
fn <- "External Direct Comparison//IndividualResults_UND.xlsx"
tmp1 <- read_excel(paste0(datapath, fn), sheet = 2, skip = 5)
fn <- "External Direct Comparison//IndividualResults_MBA.xlsx"
tmp2 <- read_excel(paste0(datapath, fn), sheet = 2, skip = 5)
tmp3 <- bind_rows(tmp1, tmp2)
names(tmp3)[1] <- "ID"

mdf <- tmp3 %>% select(-(Learner:`Student ID`)) # Remove private information

rm(list = ls(pattern = "tmp?"))
```
```{r}
fn <- "External Direct Comparison//External Direct Comparison.xlsx"
ref <- read_excel(paste0(datapath, fn), "Both")
names(ref) <- c("Course", "Timeline", "Score", "ACBSP_US", "ACBSP_R2", "US",
                "MSCHE", "Public", "Degree")
```
Create variables, reshape data set, and merge benchmark score data.
```{r}
mdf <- mdf %>%
  mutate(
    Time = ymd_hms(Completed),
    AY = case_when(
      Time %within% interval(ymd("2016-06-01"), ymd("2017-05-31")) ~ "2016",
      Time %within% interval(ymd("2017-06-01"), ymd("2018-05-31")) ~ "2017",
      Time %within% interval(ymd("2018-06-01"), ymd("2019-05-31")) ~ "2018",
      Time %within% interval(ymd("2019-06-01"), ymd("2020-05-31")) ~ "2019",
      TRUE ~ "Other"),
    Major = `Identify Your Major or Concentration`,
    Minor = `Identify Your Minor or Certificate`,
    Specialization = `MBA Specialization`,
    Degree = Program)

# Filter entries with less than 30 min spent
mdf.original <- mdf
mdf <- mdf %>% filter(`Duration (min)` > 30)

# Reshape the data
lmdf <- mdf %>% select(-c(Timeline, Faculty, Course)) %>% 
  pivot_longer(cols = c(Accounting:`Final Score`),
               names_to = "Course", values_to = "Score")
# Merge the benchmark scores and compute differences
# Need this at this stage in order to summarize prevelence of achievements
lmdf <- lmdf %>%
  left_join(ref %>% select(Course, ACBSP_US, ACBSP_R2, US, Degree),
            by = c("Degree", "Course")) %>% 
  mutate(Diff = Score - US)

# Name has changed 2019 for *General Business* to *ISBC* (along with the program
# change). Count them together.
genbus <- "(General Business)|(Integrated Global Business)|(Interdisciplinary Studies in Business and Commerce)"
lmdf <- lmdf %>%
  mutate(Major = str_replace(Major, genbus, "ISBC"),
         Degree = str_replace(Degree, "BS", "UND"))
```
Aggregate by different level (all business major, by major, by specialization).
```{r}
# Aggregate: All students
tbl1 <- lmdf %>% group_by(Degree, AY, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>%
  mutate(Major = "All", Specialization = "All")
# Disaggregate: By major
tbl2 <- lmdf %>% filter(Degree == "UND") %>% 
  group_by(AY, Major, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>% 
  mutate(Degree = "UND")
# Disaggregate: By specialization
tbl3 <- lmdf %>% filter(Degree == "MBA") %>% 
  group_by(AY, Specialization, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>% 
  mutate(Degree = "MBA")
tbl_all <- bind_rows(tbl1, tbl2, tbl3)
# tbl_und <- bind_rows(tbl1 %>% select(-Specialization), tbl2)
# tbl_mba <- bind_rows(tbl2 %>% select(-Major), tbl3)

# Re-introduce benchmark. Use only US.
ref <- ref %>% mutate(Degree = str_replace(Degree, "BS", "UND"))
tbl_all <- tbl_all %>%
  left_join(ref %>% select(Degree, Course, US),
            by = c("Degree", "Course")) %>% 
  mutate(US = US/100)
```

### Select Program

Need rework on the list to go over.

```{r}
map2 <- lmp$map_prg %>% filter(source == "External")
names(map2)
```

Compare the main group and "control group." (Need renaming...)

```{r}
# Extract relevant rows from the outcome summary
# while adding the identification information
lres <- list()
for(i in 1:nrow(map2)){
  x <- map2[i, ]
  z1 <- tbl_all %>%
    filter(Degree == "UND", Major == x$group2, Course == x$tool) %>%
    select(AY, Degree, Major, Course, n, mean, met, US) %>% 
    mutate(Program = x$program, PLO = x$plo)
  z2 <- tbl_all %>%
    filter(Degree == "UND", Major == x$external_control_group, Course == x$tool) %>%
    select(AY, Degree, Control = Major, n_ctrl = n, mean_ctrl = mean, met_contrl = met)
  lres[[i]] <- left_join(z1, z2, by = c("AY", "Degree"))
}
out_program <- bind_rows(lres) %>% arrange(Program, PLO, Major, AY)
```

```{r}
write_csv(out_program, "out/prg_external.csv")
```

### Select Core

Core is a bit different and I need to add more procedures.

```{r}
# map3 <- lmp$map_core %>% filter(source == "External")
map3 <- lmp$map_core %>% filter(group1 == "CPC")
map3
```

```{r}
# Extract relevant rows from the outcome summary
# while adding the identification information
lres <- list()
for(i in 1:nrow(map3)){
  x <- map3[i, ]
  dfx <- tbl_all %>% filter(Degree == "UND", Major == x$group2, Course == x$tool)
  lres[[i]] <- dfx %>% select(AY, Degree, Major, Course, n, mean, met, US) %>% 
    mutate(Program = x$program, PLO = x$plo, Source = x$source)
}
out_core <- bind_rows(lres) %>% arrange(Program, PLO, Major, AY)
out_core
```

Need disaggregation of assessment outcomes for core objectives.
Get the program names and corresponding major names in the Peregrine.

```{r}
lres <- list()
lmaj <- levels(factor(tbl_all$Major))
k <- 0
for(i in 1:nrow(map3)){
  x <- map3[i, ]
  for(j in 1:length(lmaj)){
    y <- lmaj[j]
    k <- k + 1
    # print(c(i, j, k))
    dfx <- tbl_all %>% filter(Degree == "UND", Major == y, Course == x$tool)
    lres[[k]] <- dfx %>% select(AY, Degree, Major, Course, n, mean, met, US) %>%
      mutate(Program = x$program, PLO = x$plo, Source = x$source)
  }
}
out_core_dis <- bind_rows(lres)
```


Merge the outcomes

```{r}
core_dis <- pivot_wider(out_core_dis, id_cols = c(AY, PLO, Source), names_from = Major, values_from = c(mean, met, n))
out_core_full <- out_core %>% left_join(core_dis, by = c("AY", "PLO", "Source")) %>% arrange(Source, PLO, AY) %>% relocate(Source, PLO, AY)
```

```{r}
write_csv(out_core_full, "out/core_external.csv")
```


### Select MBA

Specialization instead of major. Rest is the same.

```{r}
map4 <- lmp$map_mba %>% filter(group1 == "CPC")
map4
```

```{r}
# Extract relevant rows from the outcome summary
# while adding the identification information
lres <- list()
for(i in 1:nrow(map4)){
  x <- map4[i, ]
  dfx <- tbl_all %>% filter(Degree == "MBA", Major == x$group2, Course == x$tool)
  lres[[i]] <- dfx %>% select(AY, Degree, Major, Course, n, mean, met, US) %>% 
    mutate(Program = x$program, PLO = x$plo, Source = x$source)
}
out_core <- bind_rows(lres) %>% arrange(Program, PLO, Major, AY)
out_core
```


```{r}
lres <- list()
lmaj <- levels(factor(tbl_all$Specialization))
k <- 0
for(i in 1:nrow(map4)){
  x <- map4[i, ]
  for(j in 1:length(lmaj)){
    y <- lmaj[j]
    k <- k + 1
    dfx <- tbl_all %>% filter(Degree == "MBA", Specialization == y, Course == x$tool)
    lres[[k]] <- dfx %>% select(AY, Degree, Specialization, Course, n, mean, met, US) %>%
      mutate(Program = x$program, PLO = x$plo, Source = x$source)
  }
}
out_core_dis <- bind_rows(lres)
out_core_dis
```


Merge the outcomes

```{r}
core_dis <- pivot_wider(out_core_dis, id_cols = c(AY, PLO, Source), names_from = Specialization, values_from = c(mean, met, n))
out_core_full <- out_core %>% left_join(core_dis, by = c("AY", "PLO", "Source"))  %>% arrange(Source, PLO, AY) %>% relocate(Source, PLO, AY)
out_core_full
```
```{r}
write_csv(out_core_full, "out/mba_external.csv")
```

Still need improvements though.

- MBA lacking 2016
- Column names? (See the resulting sheets and find improvments)


# Next

With the updates, I have a full set of the data. Now, let's update analysis.
Archive this note and start a new one. Make the process codes independent as well.
