---
title: "Note to Produce ACBSP Standard 4 Items"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
    fig_height: 7
    fig_width: 7
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

Objective
================================================================================
It makes more sense to produce graphs and other items for ACBSP Standard 4 tables using the database, rather than using partial tables of `internal direct assessment` project. Hence, here it is.
Standard 4 "Fig 4.1" requires descriptions of PLOs, which are readily available in the dtabase file ("Mapping" tab). "Fig 4.2" requires outcomes of those PLOs.

- Create tables with multiple (3-5) data points, *separately* for each objective.
- As much possible, accompany them with sufficient information.

Set up
================================================================================
Data are semi-manually input from `external-direct-assessment` and `internal-direct-assessment` projects into the main Excel file. Use it as a database here.
```{r}
path <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Main")
summary(asm)
```

The worksheet is organized in a "long" format, convenient to work with `dplyr` and `ggplot2` paradigm. If wide tables are needed, simply filter and reshape it.
