---
title: "Note to Produce ACBSP Standard 4 Items"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
    fig_height: 7
    fig_width: 7
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

Objective
================================================================================
It makes more sense to produce graphs and other items for ACBSP Standard 4 tables using the database, rather than using partial tables of `internal direct assessment` project. Hence, here it is.
Standard 4 "Fig 4.1" requires descriptions of PLOs, which are readily available in the dtabase file ("Mapping" tab). "Fig 4.2" requires outcomes of those PLOs.

- Create tables with multiple (3-5) data points, *separately* for each objective.
- As much possible, accompany them with sufficient information.

Set up
================================================================================
Data are semi-manually input from `external-direct-assessment` and `internal-direct-assessment` projects into the main Excel file. Use it as a database here.
```{r}
path <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\WIP\\"
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Main")
summary(asm)
```

The worksheet is organized in a "long" format, convenient to work with `dplyr` and `ggplot2` paradigm. If wide tables are needed, simply filter and reshape it.

```{r}
new_names <- c('program', 'plo', 'orientation', 'type', 'ay', 'group', 'n', 'outcome', 'unit', 'target', 'goal', 'source', 'note')
asm_names <- names(asm)
names(asm_names) <- new_names # Make it into a dictionary
names(asm) <- new_names
```

```{r}
asm %>% group_by(program, orientation, type) %>% summarise(n = n(), n_PLO = n_distinct(plo), n_target = n_distinct(group)) %>% knitr::kable()
```

```{r}
x <- asm %>% filter(program == "Accounting",
                    plo == 1,
                    orientation == "External",
                    type == "Summative",
                    group == "All")

ymin <- min(x$outcome - 0.1, x$target - 0.1, na.rm = TRUE)
p <- ggplot(x, aes(ay, outcome)) +
  geom_line(na.rm = TRUE) +
  geom_point(na.rm = TRUE) +
  geom_text(aes(ay, ymin + 0.05, label = round(n, 0)),
            alpha = 0.4, na.rm = TRUE) +
  geom_hline(aes(yintercept = target),
             alpha = 0.4, color = "red", na.rm = TRUE) +
  scale_y_continuous(labels=scales::percent, limits = c(ymin, 1.01))
p
#p + facet_wrap(vars(`Learning Objective Number`)) +
#  labs(title = title, caption = caption) +
#  theme(axis.title = element_blank(),
#        text = element_text(family = "serif"),
#        panel.grid.minor.x = element_blank(),
#        legend.position = "none")
```

Moreover, updated the mapping worksheet.
```{r}
asm_map <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Mapping")
head(asm_map)
```

```{r, eval=FALSE}
# No longer valid. Skip this.
y <- asm_map %>% filter(program == "Accounting",
                    plo == "ACC 1",
                    type == "Summative")
y %>% select(description, course, external_tool, external_goal_description)
```

Hmm. Not symmetric between those worksheets. Data treats "external" vs "internal" as a category. Mapping treats them as different set of rows. I developed the latter to minimize the duplicated PLO rows, but... rows are not uniquely identified anyway.

A totally 'long' format is nice, but I won't deal with them in the same level. Meanwhile, I may want to correlate them in scatter plots. That implies I'm treating those two as distinctively different measures.

Data Update
--------------------------------------------------------------------------------
Okay, let's restructure the datasheet.

```{r}
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Sheet0")
summary(asm)
```


```{r}
names(asm)
asm %>% group_by(program, type) %>% summarise(n = n(), n_PLO = n_distinct(plo), n_group_int = n_distinct(internal_group), n_group_ext = n_distinct(external_group)) %>% knitr::kable()
```


```{r}
asm <- asm %>% mutate(ay_internal_n = paste0(ay, '\nN = ', internal_n), 
                      ay_external_n = paste0(ay, '\nN = ', external_n))
x <- asm %>% filter(plo == "ACC 1", type == "Summative") 
      
draw_graph <- function(x, orientation){
  if(nrow(x) == 0){return(NULL)}
  if(orientation == "Internal"){
    ay <- "ay_internal_n"
    outcome <- "internal_outcome"
    target <- "internal_target"
    n <- "internal_n"
  } else if (orientation == "External"){
    ay <- "ay_external_n"
    outcome <- "external_outcome"
    target <- "external_target"
    n <- "external_n"
  } else {
    return(NULL)
  }
  p <- ggplot(x, aes_string(ay, outcome)) +
    geom_line(aes(group = 1), na.rm = TRUE) +
    geom_point(na.rm = TRUE) +
    geom_hline(aes_string(yintercept = target),
               alpha = 0.4, color = "red", na.rm = TRUE) +
    scale_y_continuous(labels=scales::percent)
  p
}
draw_graph(x, "Internal")
draw_graph(x, "External")
x
```

```{r}
lx <- list()
lp <- list()
for(i in 1:nrow(asm_map)){
  i_plo <- asm_map$plo[[i]]
  i_type <- asm_map$type[[i]]
  x <- asm %>% filter(plo == i_plo, type == i_type) 
  lx[[paste(i_plo, i_type)]] <- x
  lp[[paste(i_plo, i_type)]] <- draw_graph(x, "Internal")
}
```

```{r}
lx[[1]]
lp[[1]]
```

