---
title: "Core Disaggregation"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---

# Introduction

Now that I have some data, but time insufficient to complete all the process. Given the responses from last year's retreat, I should have a higher priority on a in-depth analysis of the core results.

Let's disaggregate the core data. Finish the visualization and some analysis so that I can have a quick presentation.

# Data

Import data. New data are all stored in the Excel file under Internal Direct Assessment directory.
```{r}
knitr::opts_chunk$set(echo = FALSE)

```

```{r}
library(tidyverse)
library(readxl)
library(ggplot2)
rootpath <- "C:\\Users\\HP\\California University of Pennsylvania\\"
datapath <- paste0(rootpath, "ACBSP data reporting - Documents\\Data\\")
#
path <- paste0(datapath, "Internal Direct Assessment\\")
fn <- "Rubrics_07302021.xlsx"
rubrics <- read_xlsx(paste0(path, fn), "rubrics")
survey <- read_xlsx(paste0(path, fn), "survey")
plans <- read_xlsx(paste0(path, fn), "plans")
#
path <- datapath
fn <- "Assessment Data Main.xlsx"
sh <- c("prg", "core", "mba", "map_prg", "map_core", "map_mba", "lo_all")
maindf <- sapply(sh, function(x)
  read_xlsx(paste0(path, fn), sheet = x), USE.NAMES = TRUE)
```

**Addition**

```{r}
survey <- survey %>% filter(is.na(Exclude))
```


Clear some data issues. Note that the survey data has been manually edited to some degree.

First, simplify column names of the survey and convert types

```{r}
# ncol(survey) == 22
colnames(survey) <- c("ID", "Exclude", "Start", "Completion", "Email", "Survey Name", "Semester", "Course and Section Original", "Course and Section", "Assessment Name Original", "Assessment Name", "Rubric Grade Original", "Rubric Grade", "URL Original", "URL", "Analysis Rubric", "Action Rubric", "LO", "n", "s", "Analysis Non Rubric", "Action Non Rubric")
colnames(survey) <- make.names(colnames(survey))
survey <- survey %>% mutate(across(c(n, s), as.numeric))

# Extract ID's from URL
x <- str_match(survey$URL, "(rubricId\\=)(\\d+)")[, 3]
y <- str_match(survey$URL, "(ou\\=)(\\d+)")[, 3]
survey <- bind_cols(survey, RubricId = as.numeric(x), ou = as.numeric(y))
# Split course and section
survey <- survey %>% mutate(
  Course = paste(str_sub(Course.and.Section, 1, 3),
                 str_sub(Course.and.Section, 4, 6)),
  Section = str_sub(Course.and.Section, 8, 10))

# Split survey
survey.r <- survey %>% filter(Rubric.Grade == "Yes")
survey.n <- survey %>% filter(Rubric.Grade == "No")
# Record course IDs
clevels.r <- levels(factor(survey.r$Course))
clevels.n <- levels(factor(survey.n$Course))
```
Likewise, rubrics. There's some special character in one of columns.

```{r}
names(rubrics) <- make.names(names(rubrics))
names(rubrics)
names(rubrics)[2] <- "AssessmentId"
names(rubrics)[4] <- "Score"
names(rubrics)[11] <- "Criteria"
names(rubrics)[15] <- "Level"
```

Next, clean up the level achieved in the rubric data.

```{r}
patterns <- c(
  "Unsatisactory" = "Unsatisfactory",
  "Unsatisfactory" = "Unacceptable",
  "Advaned" = "Excellent",
  "Advanced" = "Excellent",
  "Proficient" = "Good",
  "Devloping" = "Basic",
  "Developing" = "Basic",
  "Fair" = "Basic",
  "Emerging" = "Rudimentary"
)
clean_levels <- function(x, patterns){
  z <- str_replace_all(x, "[^a-zA-Z\\s]+", "")
  z <- str_trim(z)
  z <- str_replace_all(z, patterns)
  z
}
rubrics <- rubrics %>% mutate(LevelAchieved = clean_levels(Level, patterns))

# Met
rubrics <- rubrics %>% mutate(
  Met.UND = case_when(
    is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" | LevelAchieved == "Basic" ~ "Met",
    LevelAchieved == "Rudimentary" | LevelAchieved == "Unacceptable" ~ "Not",
    TRUE ~ "Other"),
  Met.GRD = case_when(
    is.na(LevelAchieved) ~ "Missing",
    LevelAchieved == "Excellent" | LevelAchieved == "Good" ~ "Met",
    LevelAchieved == "Basic" | LevelAchieved == "Rudimentary" | LevelAchieved == "Unacceptable" ~ "Not",
    TRUE ~ "Other"),
  
  )
```

Then, combine the two for further processes.

```{r}
rubrics.orig <- rubrics
rubrics <- rubrics.orig # Prevent iterative proc
rubrics <- left_join(rubrics, survey.r, by = "RubricId", suffix = c(".rub", ".suv"))
# Split into achievements and misc like attributes
rubrics.a <- rubrics %>% filter(str_detect(Criteria, "Major|Minor|Certificate|Specialization|MBA|New Criterion|Sorting values|Diplomacy certificate", negate = TRUE))
rubrics.m <- rubrics %>% filter(str_detect(Criteria, "Major|Minor|Certificate|Specialization|MBA|New Criterion|Sorting values|Diplomacy certificate", negate = FALSE))
```

Lastly, define some misc variables.

```{r}
# Define misc
clevels.plan <- levels(factor(plans$Course))
```

## Disaggregate

Here's a new section. Associate the attributes and use them for disaggregation.

```{r}
head(rubrics.a)
```
```{r}
head(rubrics.m)
names(rubrics.m)
```

Leaving the identifiers and the attribute, trim the data.

```{r}
temp <- rubrics.m %>% select(RubricId, AssessmentId, UserId, Criteria, Level)
x <- temp %>% group_by(RubricId, AssessmentId, UserId, Criteria) %>% summarise(lvl = n_distinct(Level))

levels(factor(x$lvl))
x[x$lvl == 2, ]

rubrics.orig %>% filter(RubricId == 149547, AssessmentId == 1705767, UserId == 1822930)
rubrics %>% filter(RubricId == 149547, AssessmentId == 1705767, UserId == 1822930)
```

I cannot tell what is wrong. Exclude those samples.

```{r}
y <- x[x$lvl == 2, ]
UserExcld <- y$UserId
```

```{r}
df1 <- rubrics.a %>% filter(!UserId %in% UserExcld)
# Make the df2 wider or just trim for Major
df2 <- temp %>% filter(!UserId %in% UserExcld) %>%
  filter(Criteria == "Major") %>% 
  transmute(RubricId, AssessmentId, UserId, Major = Level)


df3 <- left_join(df1, df2, by = c("RubricId", "AssessmentId", "UserId"))

dim(df1); dim(df3)
```

```{r}
(test <- levels(factor(df2$Major)))
z <- str_replace_all(test, "[^a-zA-Z\\s]+", "")
z <- str_to_title(z)
z
str_remove(z, "Any ")
```

```{r}
patterns <- c(
  "any business majorminor" = "Business",
  "Any other business major/minor" = "Business",
  "Basic (75%)" = "Error",
  "Business (Non-Marketing)" = "Business",
  "Business Non-Marketing" = "Business",
  "Corporate Communication" = "Corporate Communication",
  "Economics" = "Economics",
  "Economics major/minor" = "Economics",
  "Finance" = "Finance",
  "Gen Bus" = "Business",
  "General Busines" = "Business",                                  
  "General business" = "Business",                                 
  "General Business" = "Business",
  "General businesss" = "Business",
  "General Businesss" = "Business",
  "Grad Student" = "Graduate Student",
  "Human Resources Management" = "HRM",
  "Integrated Global Business" = "IGBC",
  "Integrated Global Business 0%" = "IGBC",
  "Interdisciplinary Studies in Business and Commerce" = "IGBC",
  "Management" = "Management",
  "Management Information Systems" = "MIS",
  "Marketing" = "Marketing",
  "Music" = "Music",
  "Non-Business" = "Non Business",
  "Non-business major/minor" = "Non Business",
  "Non Business" = "Non Business",
  "Other" = "Other",
  "Other Business (Non-Marketing)" = "Other",
  "Other/none" = "Other",
  "Proficient (85%)" = "Error"
)
str_replace_all(test, patterns)
```

Messy. Focus on the core.

```{r}
mdf <- df3 %>% filter(Course == "BUS 499")


(test <- levels(factor(mdf$Major)))

str_replace_all(test, "[^a-zA-Z\\s]+", "")
str_replace_all(test, "General (B|b)usine(s)+", "General Business")
str_replace_all(test, "Gen Bus", "General Business")
```


```{r}
sdf <- mdf %>% mutate(
  Major = str_replace_all(Major, "[^a-zA-Z\\s]+", ""),
  Major = str_trim(Major),
  Major = str_replace_all(Major, "General (B|b)usine(s)+", "General Business"),
  Major = str_replace_all(Major, "Gen Bus", "General Business"),
  Major = str_replace_all(Major, "Interdisciplinary Studies in Business and Commerce", "General Business"),
  Major = str_replace_all(Major, "Management Information Systems", "MIS"),
  Major = str_replace_all(Major, "Human Resources Management", "HRM"),
  Major = str_replace_all(Major, "Integrated Global Business", "IGB"),
  Major = str_replace_all(Major, "Other", "General Business")
)

levels(factor(sdf$Major))
levels(factor(mdf$Assessment.Name))

```



# Report

```{r}
plolist <- maindf$map_core %>% filter(group1 == "Course")
i <- 1
x <- plolist[i, ]

head(sdf)

tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```

```{r}
i <- 2
x <- plolist[i, ]

tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```

```{r}
i <- 3
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```

```{r}
i <- 4
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```

```{r}
i <- 5
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```
```{r}
i <- 6
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```

```{r}
i <- 7
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```
```{r}
i <- 8
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```
```{r}
i <- 9
x <- plolist[i, ]
tdf <- sdf %>%
  filter(Course == x$group2,
         Assessment.Name == x$tool,
         str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                    ignore_case = TRUE)))
result <- tdf %>% group_by(Major) %>% 
  summarise(main_n = n_distinct(UserId),
            main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
criteria <- levels(factor(tdf$Criteria))

ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(x$plo)
```

## Loop

```{r}
sum_core <- function(i){
  x <- plolist[i, ]
  tdf <- sdf %>%
    filter(Course == x$group2,
           Assessment.Name == x$tool,
           str_detect(Criteria, regex(x$internal_rubric_keys2020,
                                      ignore_case = TRUE)))
  result <- tdf %>% group_by(Major) %>% 
    summarise(main_n = n_distinct(UserId),
              main_outcome = mean((Met.UND == "Met"), na.rm = TRUE))
  criteria <- levels(factor(tdf$Criteria))
  result
}
vis_core <- function(result){
  ggplot(result, aes(x = Major, y = main_outcome)) + geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + ggtitle(paste(x$plo, x$tool))
  
}


lres <- lapply(1:9, sum_core)
# lapply(lres, vis_core)


# Quick conversion for data export?
# Following the database. Each row is PLO and year. Column shows variables.
names(lres) <- paste("BUS", 1:9)

lres2 <- list()

for (i in 1:9){
  lres2[[i]] <- lres[[i]] %>% mutate(PLO = i)
}

xx <- bind_rows(lres2)

output <- pivot_wider(xx, id_cols = PLO, names_from = Major, values_from = c(main_outcome, main_n))
```


```{r}
write_csv(output, "out/core_internal.csv")
```
 
 