---
title: "Note to Update External Direct 02"
date: "9/4/2020"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
    df_print: paged
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
datapath <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
```

Objective
================================================================================
Make external direct (Peregrine CPC) graphs for ACBSP presentation.
Also, move the process from an existing project.

- [x] Add total scores to external
- [x] Add break down of BUS assessments

Data
================================================================================
Database and Mapping
--------------------------------------------------------------------------------
```{r load}
asm <- read_excel(paste0(datapath, "Assessment Data Main.xlsx"), "Outcome")
asm_map <- read_excel(paste0(datapath, "Assessment Data Main.xlsx"), "Mapping")

asm <- asm %>%
  mutate(int_delta = internal_outcome - internal_target,
         ext_delta = external_outcome - external_target)
asm <- asm %>% mutate(ay_internal_n = paste0(ay, '\nN = ', internal_n), 
                      ay_external_n = paste0(ay, '\nN = ', external_n))
```

Individual Peregrine to Summary
--------------------------------------------------------------------------------
Import individual data and benchmark scores.
```{r}
fn <- "External Direct Comparison//IndividualResults_UND.xlsx"
x1 <- read_excel(paste0(datapath, fn), sheet = 2, skip = 5)
fn <- "External Direct Comparison//IndividualResults_MBA.xlsx"
x2 <- read_excel(paste0(datapath, fn), sheet = 2, skip = 5)
x3 <- bind_rows(x1, x2)
names(x3)[1] <- "ID"

fn <- "External Direct Comparison//External Direct Comparison.xlsx"
ref <- read_excel(paste0(datapath, fn), "Both")
names(ref) <- c("Course", "Timeline", "Score", "ACBSP_US", "ACBSP_R2", "US",
                "MSCHE", "Public", "Degree")
# keys <- read_excel("data/Key mappings for Peregrine exams.xlsx")
```

Create variables, reshape data set, and merge benchmark score data.
```{r}
mdf <- x3 %>% select(-(Learner:`Student ID`)) # Remove private information
mdf <- mdf %>%
  mutate(
    Time = ymd_hms(Completed),
    AY = case_when(
      Time %within% interval(ymd("2016-06-01"), ymd("2017-05-31")) ~ "2016",
      Time %within% interval(ymd("2017-06-01"), ymd("2018-05-31")) ~ "2017",
      Time %within% interval(ymd("2018-06-01"), ymd("2019-05-31")) ~ "2018",
      Time %within% interval(ymd("2019-06-01"), ymd("2020-05-31")) ~ "2019",
      TRUE ~ "Other"),
    Major = `Identify Your Major or Concentration`,
    Minor = `Identify Your Minor or Certificate`,
    Specialization = `MBA Specialization`,
    Degree = Program)

# Filter entries with less than 30 min spent
mdf.original <- mdf
mdf <- mdf %>% filter(`Duration (min)` > 30)

# Reshape the data
lmdf <- mdf %>% select(-c(Timeline, Faculty, Course)) %>% 
  pivot_longer(cols = c(Accounting:`Final Score`),
               names_to = "Course", values_to = "Score")
# Merge the benchmark scores and compute differences
# Need this at this stage in order to summarize prevelence of achievements
lmdf <- lmdf %>%
  left_join(ref %>% select(Course, ACBSP_US, ACBSP_R2, US, Degree),
            by = c("Degree", "Course")) %>% 
  mutate(Diff = Score - US)

# Name has changed 2019 for *General Business* to *ISBC* (along with the program
# change). Count them together.
lmdf <- lmdf %>%
  mutate(Major = str_replace(Major,"Interdisciplinary Studies in Business and Commerce", "General Business"),
         Degree = str_replace(Degree, "BS", "UND"))

```

Aggregate by different level (all business major, by major, by specialization).
```{r}
# Aggregate: All students
tbl1 <- lmdf %>% group_by(Degree, AY, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>%
  mutate(Major = "All", Specialization = "All")
# Disaggregate: By major
tbl2 <- lmdf %>% filter(Degree == "UND") %>% 
  group_by(AY, Major, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>% 
  mutate(Degree = "UND")
# Disaggregate: By specialization
tbl3 <- lmdf %>% filter(Degree == "MBA") %>% 
  group_by(AY, Specialization, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>% 
  mutate(Degree = "MBA")
tbl_all <- bind_rows(tbl1, tbl2, tbl3)
# tbl_und <- bind_rows(tbl1 %>% select(-Specialization), tbl2)
# tbl_mba <- bind_rows(tbl2 %>% select(-Major), tbl3)

# Re-introduce benchmark. Use only US.
ref <- ref %>% mutate(Degree = str_replace(Degree, "BS", "UND"))
tbl_all <- tbl_all %>%
  left_join(ref %>% select(Degree, Course, US),
            by = c("Degree", "Course")) %>% 
  mutate(US = US/100)

# names(tbl_und); names(tbl_mba)
```

Outcome Table
--------------------------------------------------------------------------------

### Program Level Assessment
Using the mapping, extract relevant information.
```{r}

# With a tweak. Drop "NA" rows.
# asm_map2 <- asm_map %>% filter(course != "NA")

# Extract relevant rows from the outcome summary
# while adding the identification information
lres <- list()
for(i in c(1:nrow(asm_map))){
  # Selectors
  course <- asm_map[[i, "external_tool"]]
  degree <- asm_map[[i, "degree"]]
  major <- asm_map[[i, "external_group"]]
  control <- asm_map[[i, "external_control_group"]]
  # Identifier
  program <- asm_map[[i, "program"]]
  plo <- asm_map[[i, "plo"]]
  # Populate the list by extracting
  z1 <- tbl_all %>%
    filter(Degree == degree, Major == major, Course == course) %>%
    select(AY, Degree, Major, Course, n, mean, met, US) %>% 
    mutate(Program = program, PLO = plo)
  z2 <- tbl_all %>%
    filter(Degree == degree, Major == control, Course == course) %>%
    select(Control = Major, n_ctrl = n, mean_ctrl = mean, met_contrl = met)
  lres[[i]] <- left_join(z1, z2, by = c("AY", "Degree"))
}
x4 <- bind_rows(lres) %>% arrange(Program, PLO, Major, AY)
# x4 %>% knitr::kable(dig = 2)
```

### Core Level Assessment
Business Core assessment for each majors. First, result rows relevant. This will contain results for all business majors or MBA and by major/specialization. Then, separate the outcomes by all the business majors or MBA. Finally, 'glue' them to relevant rows (identified by degree and course/topic).
```{r}
x5 <- tbl_all %>%
  filter(Course %in% (asm_map %>% filter(core) %>% pull(external_tool)))
# x5 %>% kable(dig = 2)

ctrl <- x5 %>% filter(Major == "All") %>% select(-US) %>% 
  rename(Major_ctrl = Major, Specialization_ctrl = Specialization,
         mean_ctrl = mean, n_ctrl = n, met_ctrl = met, met_diff_ctrl = mean_diff)
x5ref <- x5 %>% select(-mean_diff) %>% 
  left_join(ctrl, by = c("Degree", "AY", "Course"))

```

Export Output Table
--------------------------------------------------------------------------------
Lastly export the output table for other use.

```{r, eval=FALSE}
write_csv(x4, "out/ext-program-assessment.csv")
write_csv(x5ref, "out/ext-core-assessment.csv")
```


Graph
================================================================================
Set Up Time Plot
--------------------------------------------------------------------------------

For time plot, a long format is more suited.
```{r}
lx4 <- pivot_longer(x4, cols = c("mean", "mean_ctrl"),
                     names_to = "Type", values_to = "mean") %>% 
  mutate(AYn = paste0(AY, "\n(n=", n, ")\n(N=", n_ctrl, ")"))
lx5ref <- x5ref %>%
  mutate(AYn = paste0(AY, "\n(n=", n, ")\n(N=", n_ctrl, ")")) %>% 
  select(Degree:mean, Major:mean_ctrl, US, AYn) %>% 
  pivot_longer(cols = starts_with("mean"),
                       names_to = "Type",
                       values_to = "mean")
```

```{r}
draw_time <- function(x, outcome,
                      ay="AY", grp = "Type", tgt="US",
                      ttl="Title", subt="Sub"){
  # Draw time plot.
  # Using the output table, varialbes needed for this functions are col names
  # Selection of data is done outside of this function
  p <- ggplot(x, aes_string(ay, outcome)) +
    geom_hline(aes_string(yintercept = tgt),
               alpha = 0.4, color = "red", na.rm = TRUE) +
    geom_line(aes_string(group = grp, linetype = grp), na.rm = TRUE) +
    geom_point(aes_string(group = grp, shape = grp), size = 2, na.rm = TRUE) +
    scale_shape_manual(values = c(16, 1), labels = c("Focus", "All Business")) +
    scale_linetype(labels = c("Focus", "All Business")) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L))
  p <- p +
    labs(title = ttl, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    ggthemes::theme_fivethirtyeight(base_size = 7) +
    theme(legend.position = "right", legend.direction = "vertical")
  p
}
```


```{r, eval=FALSE}
# Test
lo <- "BUS 1"
ori <- "External"
typ <- "Summative"
stgrp <- "Accounting" # For student group
tool <- asm_map %>% filter(plo == lo) %>% pull(external_tool_description)

ttl <- paste(lo, ori, typ)
subt <- paste0("Assessment Tool: ", tool, "\nFocus Group: ", stgrp)

# Select for plot
x <- lx5ref %>% filter(Degree == "UND", Major == stgrp,
                      Course == "Final Score")
table(x$Type)
draw_time(x, "mean", ay = "AYn", ttl = ttl, subt = subt)

# Test 2 (Graph for lx4 or program level assessment still works)
draw_time(lx4 %>% filter(PLO == "ACC 1"), "mean", ay = "AYn", grp = "Type")

# Test 3 (Focus and target are the same: Overall result)
x <- lx5ref %>% filter(Degree == "MBA", Specialization == "All",
                      Course == "Final Score")
x # Values (mean) are the same for both Type (mean, mean_ctrl)
# Need to just have one of them. Also, ggplot needs to skip grouping.
draw_time(x, "mean", ay = "AYn", ttl = ttl, subt = subt)

```

```{r}
map_draw_time <- function(x, lo, ay,
                          stgrp = NULL, crs = NULL,
                          xmap = asm_map,
                          dgr = c("UND", "MBA"),
                          typ = c("Summative", "Formative")){
  dgr <- match.arg(dgr)
  typ <- match.arg(typ)
  # Usig LO as a key, retrieve information from the mapping
  tool <- asm_map %>% filter(plo == lo, type == "Summative") %>% pull(external_tool_description)
  if(is.null(stgrp)){
    stgrp <- asm_map %>% filter(plo == lo, type == "Summative") %>% pull(external_group)
  } else{
    stgrp <- stgrp
  }
  if(is.null(crs)){
    crs <- asm_map %>% filter(plo == lo, type == "Summative") %>% pull(external_tool)
  } else{
    crs <- crs
  }
  
  if(dgr == "UND"){
    x0 <- x %>% filter(Degree == dgr, Course == crs, Major == stgrp)
  } else{
    x0 <- x %>% filter(Degree == dgr, Course == crs, Specialization == stgrp)
  }
  
  ttl <- paste(lo, "External", typ)
  subt <- paste0("Assessment Tool: ", tool, "\nFocus Group(Major/Specialization): ", stgrp)
  if(!is.na(crs)){
    draw_time(x = x0, outcome = "mean", ay = ay, ttl = ttl, subt = subt)
  } else{
    return(NULL)
  }

}
```


```{r, eval=FALSE}
# Test
map_draw_time(x = lx4, lo = "ACC 1", ay = "AYn", dgr = "UND")
map_draw_time(x = lx5ref, lo = "BUS 1", stgrp = "Accounting", ay = "AYn", dgr = "UND")
map_draw_time(x = lx5ref, lo = "MBA 1", stgrp = "General MBA", ay = "AYn", dgr = "MBA")
```


Program Level
--------------------------------------------------------------------------------
```{r, eval=FALSE}
for(key in asm_map %>% filter(type == "Summative") %>% pull(plo)){
  p <- map_draw_time(x = lx4, lo = key, ay = "AYn", dgr = "UND")
  ggsave(paste0("fig/Program/ext_", key, ".png"), p,
         height = 2, width = 3.5, units = "in")
  # print(p)
}
```

Core Level
--------------------------------------------------------------------------------
```{r, eval=FALSE}
dir.create("fig")
dir.create("fig/UND_Core")
dir.create("fig/MBA_Core")

for(grp in levels(factor(asm_map$external_group))){
  for(key in paste("BUS", 1:10)){
    p <- map_draw_time(x = lx5ref, lo = key, stgrp = grp, ay = "AYn", dgr = "UND")
    ggsave(paste0("fig/UND_Core/ext_", grp, "_", key, ".png"), p,
           height = 2, width = 3.5, units = "in")
    # print(p)
  }
}

for(grp in c("Business Analytics", "Entrepreneurship", "General MBA", "Healthcare Management", "All")){
  for(key in paste("MBA", 1:8)){
    p <- map_draw_time(x = lx5ref, lo = key, stgrp = grp, ay = "AYn", dgr = "MBA")
    ggsave(paste0("fig/MBA_Core/ext_", grp, "_", key, ".png"), p,
           height = 2, width = 3.5, units = "in")
    # print(p)
  }
}

```

Overall scores for MBA Peregrine is not in the mapping list.
```{r}
ttl <- "MBA Overall External Summative"
subt <- "Assessment Tool: CPC Exam - Final Score"

x0 <- x %>% filter(Degree == "MBA", Course == "Final Score", Specialization == "All")
p0 <- draw_time(x0, "mean", ay = "AYn", ttl = ttl, subt = subt)
ggsave("fig/MBA_Core/ext_all_final.png", p0,
       height = 2, width = 3.5, units = "in")
```

Conclusion
================================================================================
Not informative as a note, since graphs are exported for ACBSP reporting. There are just too many graphs for a note/report. It needs some focus.

