---
title: "Note to Produce ACBSP Standard 4 Items"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
    code_folding: hide
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    df_print: paged
    code_folding: hide
    fig_height: 7
    fig_width: 7
---

```{r, echo=FALSE, include=FALSE}
#knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
```

Objective
================================================================================
It makes more sense to produce graphs and other items for ACBSP Standard 4 tables using the database, rather than using partial tables of `internal direct assessment` project. Hence, here it is.
Standard 4 "Fig 4.1" requires descriptions of PLOs, which are readily available in the dtabase file ("Mapping" tab). "Fig 4.2" requires outcomes of those PLOs.

- Create tables with multiple (3-5) data points, *separately* for each objective.
- As much possible, accompany them with sufficient information.

Data
================================================================================
Main data file has been updated. Now the mapping worksheet separates internal and external assessments, aligned wit the data worksheet.
```{r}
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Sheet0")
asm_map <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Mapping")
```

Visualize
================================================================================
ACBSP Tables
--------------------------------------------------------------------------------
Create tables for ACBSP reporting.

In order to include sample sizes clearly, relabel the x-axis (Academic Year) to include sample sizes. Create new variables that have both the academic year and samples for each observation.
```{r}
asm <- asm %>% mutate(ay_internal_n = paste0(ay, '\nN = ', internal_n), 
                      ay_external_n = paste0(ay, '\nN = ', external_n))
```

Set up a template for graph.
```{r}
draw_graph <- function(x, orientation,
                       title, subtitle){
  if(nrow(x) == 0){return(NULL)}
  if(orientation == "Internal"){
    ay <- "ay_internal_n"
    outcome <- "internal_outcome"
    target <- "internal_target"
    n <- "internal_n"
  } else if (orientation == "External"){
    ay <- "ay_external_n"
    outcome <- "external_outcome"
    target <- "external_target"
    n <- "external_n"
  } else {
    return(NULL)
  }
  p <- ggplot(x, aes_string(ay, outcome)) +
    geom_line(aes(group = 1), na.rm = TRUE) +
    geom_point(na.rm = TRUE) +
    geom_hline(aes_string(yintercept = target),
               alpha = 0.4, color = "red", na.rm = TRUE) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L))
  p <- p +
    labs(title = title, subtitle = subtitle) +
    ylab("Outcome") + xlab("Academic Year\nSample Size")
  p
}
draw_from_mapping <- function(plo_map){
  i_plo <- plo_map$plo
  i_type <- plo_map$type
  int_tool <- plo_map$internal_tool
  ext_tool <- plo_map$external_tool
  
  # Make titles
  title <- paste(i_plo, i_type, collapse = " ")
  int_title <- paste(title, "Internal", collapse = " ")
  ext_title <- paste(title, "External", collapse = " ")
  int_subtitle <- paste("Assessment Tool:", int_tool)
  ext_subtitle <- paste("Assessment Tool:", ext_tool)
  
  # Draw subsample from the dataset
  x <- asm %>% filter(plo == i_plo, type == i_type) 
  # Check for empty cases, then make plot(s)
  int_p <- NULL
  ext_p <- NULL
  if (nrow(x)!=0){
    # Check for empty cases (PLO can have internal or external or both)
    if(int_tool != "NA"){
      int_p <- draw_graph(x, "Internal", int_title, int_subtitle)
      int_p <- int_p + ggthemes::theme_fivethirtyeight(base_size = 8)
    }
    if(ext_tool != "NA"){
      ext_p <- draw_graph(x, "External", ext_title, ext_subtitle)
      ext_p <- ext_p + ggthemes::theme_fivethirtyeight(base_size = 8)
    }
    out <- list(x, int_p, ext_p)
    names(out) <- c(title, int_subtitle, ext_subtitle)
    return(out)
  } else{
    return(NULL)
  }
}
```

Then, draw graphs.
```{r}
lx <- list()
lp_int <- list()
lp_ext <- list()
for(i in 1:nrow(asm_map)){
  out <- draw_from_mapping(asm_map[i, ])
  if(!is.null(out)){
    nm <- names(out[1])
    lx[[nm]] <- out[[1]]
    lp_int[[nm]] <- out[[2]]
    lp_ext[[nm]] <- out[[3]]
  }
}
```

Finally, save the graphs. Keep those chunks `eval=FALSE` for usual runs. Execute them as needed.
```{r, eval=FALSE}
lp_int[[11]] + ggthemes::theme_fivethirtyeight()
ggsave("test.png", lp_int[[11]], height = 2, width = 3.5, units = "in")
```
```{r, eval=FALSE, include=FALSE}
lapply(names(lp_int),
       function(x) ggsave(paste0("fig/", x, "_int.png"), lp_int[[x]],
                          height = 2, width = 3.5, units = "in"))
lapply(names(lp_ext),
       function(x) ggsave(paste0("fig/", x, "_ext.png"), lp_ext[[x]],
                          height = 2, width = 3.5, units = "in"))
```

Next
================================================================================

