---
title: 'Assessment Analysis Case: Business Core'
author: "Kentaro Murayama"
date: "8/5/2020"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
---

# Assessment Visualization

We would like to assess and develop our curriculum.

## Standard 4: Student Learning Assessment

> The business unit must have a systematic student learning outcomes assessment
process and plan that leads to continuous improvement. Student learning outcomes
must be developed and implemented for each accredited program, and the results
must be communicated to stakeholders.


## Standard 6: Curriculum

> The business unit must have a systematic process to ensure continuous
improvement of curriculum and program delivery. The curriculum must be comprised
of appropriate business and professional content to prepare graduates for
success.

<https://acbsp.org/general/custom.asp?page=accreditation-standards>

--

**i.e. Past and Data &rarr; Future and Strategy.**

---

# Assessment?

## Assessment Structure

- Program Goals
- Program Learning Objectives
- (Course Objectives)
- Assessment/Rubric

## Examples of Data Types

|            | Internal | External |
|---|---|---|
| Formative  | MBA Final Exams | |
| Summative  | Sig. Assignments | CPC Exams |
|---|---|---|
| Indirect  |                  | Survey    |

---

# Assessment Visualization

Or more...

- Operational key performance indicators
    - Graduation Rates
    - Retention Rates
    - Enrollment
- Stakeholder satisfaction
    - Student satisfaction
    - Alumni satisfaction
- Faculty and staff focus
    - Professional development
    - Scholarly activity
    - Faculty qualifications
- Support key performance indicators
    - Computer support
    - Library research support
    - Administrative support
    
<https://acbsp.org/general/custom.asp?page=outcomes_assessment>

---

# Assessment Visualization

## Data Presented Here

Assessment Outcomes for Business Core (BUS 499) are presented to show the following:

- Trends Over Time
- Associations by Type
- Comparisons against Target Levels

--

## Goals

- To share the insights for Business Core results with everyone
- To explain the data presentation used in each program reports
- To demonstrate the type of analysis we will do in the following session
- To gather feedback from everyone to improve the processes above

---
exclude: true

# Set up

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
```
```{r load, cache=TRUE}
path <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\WIP\\"
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Sheet0")
asm_map <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Mapping")

asm <- asm %>%
  mutate(int_delta = internal_outcome - internal_target,
         ext_delta = external_outcome - external_target)
asm <- asm %>% mutate(ay_internal_n = paste0(ay, '\nN = ', internal_n), 
                      ay_external_n = paste0(ay, '\nN = ', external_n))
prg <- "Business Core"
```
```{r corr}
draw_corr <- function(prg, ty = c("Summative", "Formative", "Both")){
  type <- match.arg(ty)
  # Select samples and 
  if (ty == "Both"){
    x <- asm %>% filter(program == prg)
  } else {
    x <- asm %>% filter(program == prg, type == ty)
  }
  if (all(is.na(x$external_outcome)) |
      all(is.na(x$internal_outcome))){
    return(NULL)}
  
  xmin <- min(x$internal_outcome, x$internal_target)
  ymin <- min(x$external_outcome, x$external_target)
  
  title <- paste(prg, type, "External vs Internal")
  subtitle <- "Assessment outcomes are plotted to each other."
  subtitle <- paste0(subtitle, "\nRed point is the 2019 result")
  
  p <- ggplot(x, aes(internal_outcome, external_outcome)) +
    geom_path(linetype = "longdash", na.rm = TRUE) +
    geom_point(aes(color = ay == 2019), na.rm = TRUE) +
    scale_color_manual(values = c("black", "red")) +
    geom_hline(aes(yintercept = external_target), color = "black", alpha = 0.3) +
    geom_vline(aes(xintercept = internal_target), color = "black", alpha = 0.3)
  p <- p +
    facet_wrap(vars(plo))
  p + 
    labs(title = title, subtitle = subtitle) +
    xlab("Internal Assessment Outcomes") +
    ylab("External Assessment Outcomes") +
    scale_x_continuous(breaks = 1:10/10,
                       labels=scales::percent_format(accuracy = 5L)) +
    scale_y_continuous(breaks = 1:10/10,
                       labels=scales::percent_format(accuracy = 5L)) +
    coord_cartesian(xlim = c(xmin - 0.05, 1.01), ylim = c(ymin - 0.05, 1.01)) +
    theme_minimal() +
    theme(legend.position = "none",
          aspect.ratio = 1)
}
# draw_corr("Human Resources Management", "Both")
# draw_corr("Accounting", "Summative")
```
```{r delta}
list_plo <- function(prg){
  asm_map %>% filter(program == prg) %>%
    select(plo, description, ends_with("tool_description")) %>%
    knitr::kable()
}
draw_delta <- function(prg, yr = 2019, ori = c("External", "Internal")){
  type <- match.arg(ori)
  
  if (ori == "External"){
    delta <- "ext_delta"
  } else {
    delta <- "int_delta"
  }
  
  title <- paste(prg, ori, "for", yr)
  subtitle <- "Differences between target achievements and actual outcomes"
  
  x <- asm %>% filter(program == prg, ay == yr)
  x <- x %>% mutate(plo = ordered(str_extract(plo, "\\d{1,2}"), levels = 1:10))
  p <- ggplot(x, aes_string("plo", delta)) +
    geom_col(na.rm = TRUE) +
    geom_hline(yintercept = c(-0.2, 0.2), color = "red", alpha = 0.5) +
    geom_hline(yintercept = 0.0, color = "black", alpha = 0.4)
  p +
    labs(title = title, subtitle = subtitle) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L),
                       breaks = -5:5/10) +
    ggthemes::theme_fivethirtyeight(base_size = 8) +
    theme(legend.position = "none")
}
combine_deltas <- function(prg, yr = 2019){
  p1 <- draw_delta(prg, yr, "External")
  p2 <- draw_delta(prg, yr, "Internal")
  gridExtra::grid.arrange(p1, p2, ncol = 2)
}
# draw_delta("Business Core", ori = "External")
# draw_delta("Human Resources Management", ori = "Internal")
```
```{r time}
draw_time <- function(lo, ori = c("External", "Internal"),
                      typ = c("Summative", "Formative")){
  ori <- match.arg(ori)
  typ <- match.arg(typ) 
  if (ori == "External"){
    outcome <- "external_outcome"
    target <- "external_target"
    ay <- "ay_external_n"
  } else {
    outcome <- "internal_outcome"
    target <- "internal_target"
    ay <- "ay_internal_n"
  }
  x <- asm %>% filter(plo == lo, type == typ)
  if (all(is.na(x$external_outcome)) |
      all(is.na(x$internal_outcome))){
    return(NULL)}
  p <- ggplot(x, aes_string(ay, outcome)) +
    geom_line(aes(group = 1), na.rm = TRUE) +
    geom_point(size = 2, na.rm = TRUE) +
    geom_hline(aes_string(yintercept = target),
               alpha = 0.4, color = "red", na.rm = TRUE) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L))
  p + ggthemes::theme_fivethirtyeight()
  p
}
combine_time <- function(lo, typ){
  x <- asm_map %>% filter(plo == lo, type == typ)
  title <- paste(lo, typ, "Assessment Outcomes")
  title <- paste0(title,
                  str_sub(paste0("\n(", x %>% pull(description)), 1, 50), "...)" )
  p1 <- draw_time(lo, "Internal", typ)
  p2 <- draw_time(lo, "External", typ)
  if (is.null(p1) & is.null(p2)){
    return(NULL)
  }
  if (is.null(p1)){
    p1 <- ggplot() + theme_void()
  } else{
    p1 <- p1 +
      ylab("Internal") +
      xlab("Academic Year\nSample Size") +
      theme(plot.title = element_blank(),
            plot.subtitle = element_blank(),
            axis.title.x = element_blank(),
            legend.position = "none") +
      ggthemes::theme_fivethirtyeight(base_size = 16)
  }
  if (is.null(p2)){
    p2 <- ggplot() + theme_void()
  } else{
    p2 <- p2 +
      ylab("External") +
      xlab("Academic Year\nSample Size") +
      theme(plot.title = element_blank(),
            plot.subtitle = element_blank(),
            axis.title.x = element_blank(),
            legend.position = "none") +
      ggthemes::theme_fivethirtyeight(base_size = 16)
  }
  gridExtra::grid.arrange(p1, p2, ncol = 1, top = title)
}
gather_times <- function(prg){
  lplo <- asm_map %>% filter(program == prg) %>% pull(plo)
  ltyp <- asm_map %>% filter(program == prg) %>% pull(type)
  for (i in 1:length(lplo)){
    combine_time(lplo[i], ltyp[i])
  }
}
# gather_times("Human Resources Management")
```

```{r}
draw_time2 <- function(lo, ori, typ){
  if (ori == "External"){
    subt <- asm_map %>% filter(program == prg, plo == lo) %>%
      pull(external_tool_description)
  } else {
    subt <- asm_map %>% filter(program == prg, plo == lo) %>%
      pull(internal_tool_description)
  }
  p <- draw_time(lo, ori, typ)
  p <- p +
    labs(title = ori, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    theme(plot.title = element_blank(),
          plot.subtitle = element_blank(),
          axis.title.x = element_blank(),
          legend.position = "none") +
    ggthemes::theme_fivethirtyeight(base_size = 18)
  p
}
```
```{r}
draw_corr2 <- function(lo, ty = c("Summative", "Formative", "Both")){
  type <- match.arg(ty)

  if (ty == "Both"){
    x <- asm %>% filter(plo == lo)
  } else {
    x <- asm %>% filter(plo == lo, type == ty)
  }
  if (all(is.na(x$external_outcome)) |
      all(is.na(x$internal_outcome))){
    return(NULL)}
  
  xmin <- min(x$internal_outcome, x$internal_target)
  ymin <- min(x$external_outcome, x$external_target)
  
  title <- "External vs Internal"
  caption <- "(Grey lines: Target levels; Red point: 2019 result)"
  
  p <- ggplot(x, aes(internal_outcome, external_outcome)) +
    geom_path(linetype = "longdash", na.rm = TRUE) +
    geom_point(aes(color = ay == 2019), na.rm = TRUE) +
    scale_color_manual(values = c("black", "red")) +
    geom_hline(aes(yintercept = external_target), color = "black", alpha = 0.3) +
    geom_vline(aes(xintercept = internal_target), color = "black", alpha = 0.3)
  p + 
    labs(title = title, caption = caption) +
    xlab("Internal Assessment Outcomes") +
    ylab("External Assessment Outcomes") +
    scale_x_continuous(breaks = 1:10/10,
                       labels=scales::percent_format(accuracy = 5L)) +
    scale_y_continuous(breaks = 1:10/10,
                       labels=scales::percent_format(accuracy = 5L)) +
    coord_cartesian(xlim = c(xmin - 0.05, 1.01), ylim = c(ymin - 0.05, 1.01)) +
    ggthemes::theme_fivethirtyeight(base_size = 12) +
    theme(axis.title = element_text(),
          legend.position = "none",
          aspect.ratio = 1)
}
# draw_corr2("BUS 1", "Summative")
```

---

# Demonstration: BUS 5 Summative
```{r}
lo <- "BUS 5"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
- Good improvements both in internal and external assessment outcomes.
- External assessment - based on a CPC exam section - remains higher than the target level, US Average.
- However, the achievements appear to be rather extreme.
    - Nearly 20 percentage points above the US average and
    - improvement by 10 percentage points in a year.
    
Suggestive Improvement: Have a video monitoring to assure the fair assessment process.

]

---

# Demonstration: BUS 5 Summative
```{r}
lo <- "BUS 5"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
- Internal assessment outcomes - capstone instrument Company Profile assignment - have improved over time, passing the target level in  academic year 2018 and continued the improvement in 2019.
- Target achievement level is appropriate, given a moderate level of "excess" achievements.

Suggestive Improvement: Implement additional analyses (e.g. consistency among instructors, rubric row specific comparison of students' outcomes) and refine the assessment.

]

---

# Demonstration: BUS 5 Summative

```{r}
lo <- "BUS 5"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ) + geom_text(aes(label = ay), nudge_x = 0.05)
```

Plot of internal vs external assessment outcomes over time.
]
.pull-right[
**What am I seeing?**

- Red point shows the combination of internal and external assessment outcomes for the academic year 2019: 85% Internal & 80% External
- Other dots show the combinations over time: 2018, 2017, and 2016, following the broken line
]

---

# Demonstration: BUS 5 Summative

```{r}
lo <- "BUS 5"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ) + annotate("segment", x = 0.50, xend = 0.85, y = 0.63, yend = 0.78, colour = "orange", size=2, alpha=0.7, arrow=arrow())
```

Plot of internal vs external assessment outcomes over time.
]
.pull-right[
**What do I get out of this picture?**

- Overall trend from bottom-left to upper-right: From 2016 to 2019, both the external and internal assessment outcomes have improved
- Rather flat line: However, the change in the internal assessment outcomes have been overwhelmingly strong

]

---

# Demonstration: BUS 5 Summative

```{r}
lo <- "BUS 5"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```

Plot of internal vs external assessment outcomes over time.
]
.pull-right[
**So what?**

Let's suppose 
1. the external assessments measure basic knowledge of students (e.g. what does A mean?), while
2. internal assessments measure applied knowledge (e.g. how can/would you use A in business?).

Then, this picture implies that Business Core improved its process so that students can utilize their knowledge to analyze business situations and communicate solutions.

]

---

# Enough Talk, Show Me Data

Alright, I'll show Business Core PLO 1-10 outcomes and discuss very briefly.

Please type into chat if you have anything you'd like to add.

---

# BUS 1 Summative

```{r}
lo <- "BUS 1"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]


---

# BUS 2 Summative

```{r}
lo <- "BUS 2"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 3 Summative
```{r}
lo <- "BUS 3"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```

]

---

# BUS 4 Summative
```{r}
lo <- "BUS 4"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 5 Summative
```{r}
lo <- "BUS 5"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 6 Summative
```{r}
lo <- "BUS 6"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 7 Summative
```{r}
lo <- "BUS 7"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 8 Summative
```{r}
lo <- "BUS 8"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 9 Summative
```{r}
lo <- "BUS 9"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---

# BUS 10 Summative
```{r}
lo <- "BUS 10"
typ <- "Summative"
dsc <- asm_map %>% filter(program == prg, plo == lo) %>% pull(description)
```
`r dsc`

.pull-left[
```{r, fig.height=4}
draw_time2(lo, "Internal", typ)
```
```{r, fig.height=4}
draw_time2(lo, "External", typ)
```
]
.pull-right[
```{r, fig.width=5, fig.height=5}
draw_corr2(lo, typ)
```
]

---
# Where Are We Standing Now?

Next, I'll show a "snapshot" of the PLO outcomes for academic year 2019.

I took the differences between the actual outcomes and target levels.

---
class: center

# Snapshot of Academic Year 2019
```{r, fig.width=9, fig.height=5}
combine_deltas(prg)
```

- All PLO outcomes fulfilled the targets both in external and internal assessments.
- Inflating grades in CPC exams are evident. Even the lowest is close to 10 percentage points above the US average (BUS 9 Organizational behavior)
- Internal assessments for BUS 1 & 2 outcomes exceed the target by more than 20 percentage points. It may need re-evaluation.



---
exclude: true

# Disaggregation by Majors
```{r}
# Run int_prepare.R if not available
disag <- readRDS("../out/disag.Rds")
disag <- disag %>% mutate(PLO = paste0("BUS ", PLO, "\nn=", n))
draw_disag <- function(prg){
  title <- paste("Business Core Outcome for", prg, "Majors")
  p <- ggplot(disag %>% filter(Major == prg), aes(factor(PLO), Met - 0.7)) +
    geom_col()
  p + 
    labs(title = title) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L),
                       breaks = -5:5/10) +
    ggthemes::theme_fivethirtyeight(base_size = 8) +
    theme(legend.position = "none")
  
}
# draw_disag("Marketing")
```

---
exclude:true

```{r, eval=FALSE}
pagedown::chrome_print("presentation-business-core-2.html",
                       output="out/slides-demonstration.pdf")
```

---

# Thank You

After all the presentations, we will discuss in *breakout rooms* forming groups by specialty/program.

Please use the Word files placed in "Strategy Meeting 2020 Summer/20200805 Session 1 Aug 5" folder to record your discussions.

