---
title: "Test Importing New Data Format"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---

# Introduction

Due to the computer crush, I lost the recent notes on importing the new data format. Let's go over this again. Jon tested the new D2L data format with me and came up with a reasonably good solution. The item at hand should have all the necessary information.

Fist, I need to verify the data are here.
Then, I need to clean the data.
Third, the data will be stored in a database, so that others can use it without going through the cleaning process.
Fourth, make a set of reports, using the scripts from the last iteration.

# Import Data

```{r}
library(tidyverse)
library(readxl)
rootpath <- "C:\\Users\\HP\\California University of Pennsylvania\\"
datapath <- paste0(rootpath, "ACBSP data reporting - Documents\\Data\\")
path <- paste0(datapath, "Internal Direct Assessment\\")
fn <- "Rubrics_07302021.xlsx"
rubrics <- read_xlsx(paste0(path, fn), "rubrics")
  # mutate(across(c(RubricId:Name, LevelAchieved), factor),
  #        IsScoreOverridden = (IsScoreOverridden == "True"))
survey <- read_xlsx(paste0(path, fn), "survey")
```


Check the data:

```{r}
head(rubrics)
names(rubrics)
```

```{r}
head(survey)
names(survey)
survey
```

I'll standardize the survey this summer, so that those are all standardized. Anyway, let's worry about it later. Next, clean the rubrics data.

# Clean Data
## First Impression

```{r assignment-names}
# table(rubrics$Name)
levels(factor(rubrics$Name))
```

```{r}
# table(rubrics$`Rubric Object Criteria 6-Name`)
levels(factor(rubrics$`Rubric Object Criteria 6-Name`))
```

```{r}
# table(rubrics$`Rubric Object Levels 6-Name`)
levels(factor(rubrics$`Rubric Object Levels 6-Name`))
```

As expected, it's quite a mess. Let's figure out priorities.

1. Standardize the assessment names, following the plan. Refer to the Excel sheet and convert them.
2. Drop the non-assessment courses and assignments.
3. Standardize the achievement levels. This should be easy with the existing script.

Alternatively, I can merge the survey using the keys and filter. Then, I can do steps 1 and 2.

## Merge and Filter

```{r}
mdf <- survey %>% select(ID, Exclude, Email, Name, Semester, "Course and Section", "Assignment Names", "URL")

x <- head(mdf$URL)
str_extract(x, "rubricId\\=\\d+")
str_extract(x, "ou\\=\\d+")
str_match(x, "(ou\\=)(\\d+)")
```

```{r}
rubricId <- str_match(mdf$URL, "(rubricId\\=)(\\d+)")[, 3]
ou <- str_match(mdf$URL, "(ou\\=)(\\d+)")[, 3]

mdf <- bind_cols(mdf, RubricId = rubricId, ou = ou)
mdf <- mdf %>% mutate(RubricId = as.numeric(RubricId))

survey.backup <- mdf
```

```{r}
head(mdf)
```

Now merge.

```{r}
levels(factor(rubrics$RubricId))
```

```{r}
levels(factor(mdf$RubricId))
```

```{r}
rubrics <- left_join(rubrics, mdf, by = "RubricId", suffix = c(".rub", ".suv"))
# with(rubrics, table(RubricId, Code))
head(rubrics)
```


```{r}
levels(factor(rubrics$`Assignment Names`))
```

Just realized a mistake. I need to also connect to the learning objectives, using the search key in the main database. That may take a while...
Also, I can't filter out based on the survey. Those are all requested.

Anyway, the first step is the same. Let's clean up the assignment names.

## Clean Assignment Names

```{r}
courses <- str_split(rubrics$`Course and Section`, "-", simplify = TRUE)
rubrics <- bind_cols(rubrics, Course = courses[, 1], Section = courses[, 2])

rubrics %>% filter(Course == "BUS499")
(clevels <- levels(factor(rubrics$Course)))
```

18 courses to go through.

This is something that can be simplified/standardized in the survey. For this iteration, let's just edit manually. Sort the data by course. Standardize names.


```{r}
x <- rubrics %>% filter(Course == "BUS345")
levels(factor(x$`Assignment Names`))
```


```{r}
x <- rubrics %>% filter(Course == "BUS499")
levels(factor(x$`Assignment Names`))
```

```{r}
x <- rubrics %>% filter(Course == "FIN301")
levels(factor(x$`Assignment Names`))
```

Why do we have 301? And this name conflict again.


```{r}
x <- rubrics %>% filter(Course == "HRM400")
levels(factor(x$`Assignment Names`))
```


```{r}
x <- rubrics %>% filter(Course == "MBA700")
levels(factor(x$`Assignment Names`))
```
```{r}
x <- rubrics %>% filter(Course == "MKT300")
levels(factor(x$`Assignment Names`))
```

Now, reload and examine.

Clean enough.

## Achievement Levels

Next, clean achievement levels. Apply this part to the rubric data directly later and save as the source data. This way, I can have clean survey and clean rubric.


```{r}
head(rubrics)
clevels
```


```{r}
mdf <- rubrics %>% select(Course, Section, Semester, Assignment = `Assignment Names`, Criteria = `Rubric Object Criteria 6-Name`)
head(mdf)
```

```{r}
sdf <- mdf %>% filter(Course == "ACC441")
head(sdf)
levels(factor(sdf$Criteria))
```

No rubric provided last time.
Other ones are exams.

```{r}
sdf <- mdf %>% filter(Course == "ECO421")
head(sdf)
levels(factor(sdf$Criteria))

```

- All rows.
- Lit review.
- Discussion.

Same keys.



```{r}
sdf <- mdf %>% filter(Course == "FIN302")
head(sdf)
levels(factor(sdf$Criteria))
```

No rubric last time.


```{r}
sdf <- mdf %>% filter(Course == "HRM400")
levels(factor(sdf$Assignment))
```


```{r}
tdf <- sdf %>% filter(Assignment == "Final Project Proposal")
levels(factor(tdf$Criteria))
tdf <- sdf %>% filter(Assignment == "Simulation Paper 1")
levels(factor(tdf$Criteria))
levels(factor(tdf$Semester))
levels(factor(tdf$Section))
tdf <- sdf %>% filter(Assignment == "Simulation Paper 2")
levels(factor(tdf$Criteria))
levels(factor(tdf$Semester))
levels(factor(tdf$Section))
tdf <- sdf %>% filter(Assignment == "Simulation Paper 3")
levels(factor(tdf$Criteria))
levels(factor(tdf$Semester))
levels(factor(tdf$Section))
```

No need for consolidation.



```{r}
sdf <- mdf %>% filter(Course == "BUS345")
levels(factor(sdf$Assignment))
# levels(factor(sdf$Criteria))
```


```{r}
tdf <- sdf %>% filter(Assignment == "Annotated Bibliography")
levels(factor(tdf$Criteria))
```

Use keys.

```{r}
tdf <- sdf %>% filter(Assignment == "Ethics Final Paper")
levels(factor(tdf$Criteria))
```


```{r}
sdf <- mdf %>% filter(Course == "MKT401")
levels(factor(sdf$Assignment))
levels(factor(sdf$Criteria))
```

Such a mess, but use the same keys.



No use. Let's use the existing keys to produce outputs and see issues later.

## Duplicates

```{r}
names(survey.backup)
table(survey.backup$RubricId)
```

Check survey. Flag.

```{r}
survey.backup %>% filter(RubricId == 138337)
```

```{r}
survey.backup %>% filter(RubricId == 138340)
```

```{r}
survey.backup %>% filter(RubricId == 138341)
```

```{r}
survey.backup %>% filter(RubricId == 138343)
```
```{r}
survey.backup %>% filter(RubricId == 138344)
```

```{r}
survey.backup %>% filter(RubricId == 149547 )
```
Problem. Two different assignments.
MGT300-GW1	Hidden Figures Paper 
MGT300-GW1	Power and Influence AAR

```{r}
survey.backup %>% filter(RubricId == 155080)
```
```{r}
survey.backup %>% filter(RubricId == 155081)
```
```{r}
survey.backup %>% filter(RubricId == 160156)
```

```{r}
survey.backup %>% filter(RubricId == 163227)
```
```{r}
survey.backup %>% filter(RubricId == 169074)
```

This one is problematic. Supposed to be different assignment, but duplicated.

FIN301-GW1	Moral Hazard 
FIN301-GW1	RIch Uncle

```{r}
survey.backup %>% filter(RubricId == 171642)
```

Now, check.

```{r}
test <- survey.backup %>% filter(is.na(Exclude))
table(test$RubricId)
plot(table(test$RubricId))
```


```{r}
survey.backup %>% filter(RubricId == 164867)
```
```{r}
survey.backup %>% filter(RubricId == 148858)
```

```{r}
survey.backup %>% filter(RubricId == 180495)
```

Supposed to be different.
BUS242-GW1	Second Paper and presentation
BUS242-GW1	Second Paper and presentation


Check again. Done.

# Next

The data should be fairly clean.

- Compile data using keys. Check for errors.
- Ask for the correct URLs for the duplicates. No rush at this point.
- Ask for Exam data. This is urgent.

Archive this document and move on.
