---
title: "Test AY21 data"
output: html_notebook
---

# Introduction

The data format should be the same as last year (AY20). Let's verify the format and the data completeness.
Notes from last year are a bit of mess. For now, let's copy some scripts and focus on data check. Later, I can have some updates to the scripts (and source data format).

# Import Data

```{r}
library(tidyverse)
library(readxl)
rootpath <- "C:\\Users\\HP\\California University of Pennsylvania\\"
datapath <- paste0(rootpath, "ACBSP data reporting - Documents\\Data\\")
path <- paste0(datapath, "Internal Direct Assessment\\")
fn <- "RubricsAY21.xlsx"
rubrics <- read_xlsx(paste0(path, fn), "rubrics")
  # mutate(across(c(RubricId:Name, LevelAchieved), factor),
  #        IsScoreOverridden = (IsScoreOverridden == "True"))
fn <- "SurveyAY21.xlsx"
survey <- read_xlsx(paste0(path, fn))

head(rubrics)
dim(rubrics)
head(survey)
```

The first impression is not bad. Let's check the rubric ID match.

```{r}
nlevels(factor(survey$RubricId))
nlevels(factor(rubrics$RubricId))
```

Some rubrics are not found the retrieved data.

```{r}
x <- levels(factor(survey$RubricId))
y <- levels(factor(rubrics$RubricId))
z <- x[!(x %in% y)]
```

```{r}
survey %>% filter(RubricId %in% z)
```

Okay, some of no-rubric cases are picked up. The situation is not as bad.

List up the entries that are missing in the rubric data.

```{r}
missing <- survey %>% filter(RubricId %in% z, Rubric == "Yes") %>%
  select(Email, Name1, Name2, Section, ou, RubricId, URL)
missing
# write.csv(missing, file = "missing.csv")
```

Let's ask Jon about them. Several of them are rather unlikely.


