---
title: "Report 01 Summative Assessments 2020 for BEES"
author: "Kentaro Murayama"
date: "12/19/2020"
output: html_document
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
root <- "C:\\Users\\kentr\\California University of Pennsylvania\\"
datadir <- "ACBSP data reporting - Documents\\Data\\"
datapath <- paste0(root, datadir)
```

# Introduction

Summative assessments are summarized in this document.
All the values for assessment outcomes are stored in an Excel file.
Scripts to create new values are stored in this project under `R` directory.

# Data

Load data from sheets.
One list for the values and the other for mappings.

```{r load}
# File names and worksheet names
fn <- paste0(datapath, "Assessment Data Main.xlsx")
sns <- c("prg", "core", "mba")
mns <- paste0("map_", sns)

# Load data and mappings into lists
ldf <- sapply(sns, function(x) read_excel(fn, x),
              simplify = FALSE, USE.NAMES = TRUE)
lmp <- sapply(mns, function(x) read_excel(fn, x),
              simplify = FALSE, USE.NAMES = TRUE)
```

Data is stored in a simple two-way (flat) table. Visualization can be done in Excel easily.

```{r}
sapply(ldf, names)
```


# Summary Visualization

```{r}
draw_time <- function(sn, i, y1 = "main", y2 = NULL){
  # Pick a row from mapping
  x <- lmp[[paste("map", sn, sep = "_")]][i, ]
  # Using the information, pick relevant data and comparison if any
  y <- ldf[[sn]] %>% filter(plo == x$plo, type == x$type, source == x$source)
  if(!is.null(y2)){
    y <- y %>% select(plo, type, source, ay, starts_with(c(y1, y2)))
  }
  # Reshape with main/comparison distinctions in outcome
  z <- pivot_longer(y, cols = ends_with("outcome"),
                    names_to = "Type", values_to = "Outcome")
  
  p <- ggplot(z, aes(ay, Outcome, group = Type)) +
    geom_line(aes(linetype = Type), na.rm = TRUE) +
    geom_point(size = 2, na.rm = TRUE) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L)) 
  # Using the map (x), add the target level
  p <- p + geom_hline(aes(yintercept = x$target), alpha = 0.4, color = "red")
  
  ttl <- paste(x$plo, x$type, x$source)
  subt <- paste0("Assessment Tool: ", x$tool_description)
  p + labs(title = ttl, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    ggthemes::theme_fivethirtyeight(base_size = 7) +
    theme(legend.position = "right", legend.direction = "vertical")
}

# Test
# draw_time("prg", 1)
# draw_time("prg", 25, y2 = "all")
# draw_time("core", 1)
# draw_time("core", 1, y2 = "acc")
# draw_time("core", 1, y2 = c("acc", "eco"))
# draw_time("mba", 1)
# draw_time("mba", 1, y2 = "ba")
```


