---
title: "Note to Update Internal Indirect 01"
date: "9/3/2020"
output:
  html_document:
    toc: yes
    df_print: paged
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
datapath <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
```

Objective
================================================================================
Make internal indirect (exit survey) graphs for ACBSP presentation.
Also, move the process from an existing project.

- [x] Add survey graphs to goals

Data
================================================================================
First, load the data. Also, set some parameters for later use.
```{r}
path <- paste0(datapath, "Internal Indirect Assessment\\")
fn1 <- "Full 2018-2020 MBA student survey.xlsx"
fn2 <- "Full 2018-2020 UND student survey.xlsx"
# Group survey questions for display
idx <- list(Program = c(17, 18, 21, 22), Schedule = c(15, 27),
            Advising = c(25, 28),
            Courses = c(16, 20, 26), Student = c(19, 23, 24),
            Outcome1 = 29:32, Outcome2 = 33:36)
qidx <- sapply(idx, function(x) paste0("Q", x))

# Import data
df1 <- read_excel(paste0(path, fn1), "Raw Results")
df2 <- read_excel(paste0(path, fn2), "Raw Results")
# Merge data
mdf <- bind_rows(df1, df2)
```

Then, create categories of interest (semesters) and order responses.
```{r}
responses <- c("Strongly Disagree", "Disagree", "Neutral",
               "Agree", "Strongly Agree")
ys <- c("2018 Fall", "2019 Spring", "2019 Summer", "2019 Fall", "2020 Spring")
# Merge data and rename variables, while keeping questions in a vector
questions <- names(mdf)
questions <- paste0(rep("Q", length(questions)), 1:length(questions),
                    " ", questions)
names(mdf) <- paste0("Q", 1:ncol(mdf))

# Add some new variables
mdf <- mdf %>% mutate(
  ID = 1:nrow(mdf), 
  Time = mdy(Q1), Month = month(Time), Year = year(Time), 
  Semester = case_when(Month < 6 ~ "Spring",
                       Month > 5 & Month < 9 ~ "Summer",
                       TRUE ~ "Fall"),
  nSemester = case_when(Semester == "Spring" ~ 1,
                        Semester == "Fall" ~ 3,
                        Semester == "Summer" ~ 2),
  YS = paste(Year, Semester),
  AY = case_when(
    YS == "2018 Summer" | YS == "2018 Fall" | YS == "2019 Spring" ~ 2018,
    YS == "2019 Summer" | YS == "2019 Fall" | YS == "2020 Spring" ~ 2019 ),
  nYS = Year * 10 + nSemester
  )

# Format variable types
mdf <- mdf %>%
  mutate_at(vars(Q15:Q36), ordered, responses) %>% 
  mutate_at(vars(YS), ordered, ys) %>% 
  mutate_at(vars(Month, Year, AY), ordered)
```

Graph
================================================================================
```{r}
# Prepare for a long-format data of categorical answers
lmdf <- mdf %>%
  pivot_longer(cols = Q15:Q36, names_to = "QID", values_to = "Answer") %>% 
  mutate(Question = factor(QID, levels = paste0("Q", 15:36),
                           labels = questions[15:36]),
         Agreed = ifelse(Answer == "Agree" | Answer == "Strongly Agree", 1, 0))

mba <- lmdf %>% filter(!is.na(Answer) & Q2 == "MBA")
und <- lmdf %>% filter(!is.na(Answer) & Q2 == "BS" & Semester != "Summer")
```
```{r}
# Create frequency tables to reduce time for plotting
tbl.mba.agreed <- mba %>% group_by(Question, QID, nYS, YS) %>%
  summarise(Agreed = mean(Agreed), n = n())
tbl.mba.answer <- mba %>% group_by(nYS, YS, Question, QID, Answer) %>%
  summarise(n = n())
tbl.und.agreed <- und %>% group_by(Question, QID, nYS, YS) %>%
  summarise(Agreed = mean(Agreed), n = n())
tbl.und.answer <- und %>% group_by(nYS, YS, Question, QID, Answer) %>%
  summarise(n = n())
```
```{r}
draw_graph <- function(x_answer, x_agreed, title = element_blank()){
  # Wrapper function to draw graphs in a consistent format
  caption <- "Grey number shows the sample size.\nRed horizontal line indicates the goal: at least 80% of students agree or strongly agree."
  p <- ggplot() +
    geom_col(data = x_answer, aes(YS, n, fill = Answer), position = "fill") +
    scale_fill_brewer(palette = "RdYlBu", drop = FALSE)
  p <- p +
    geom_hline(yintercept = 0.8, color = "red", alpha = 0.8) +
    geom_line(data = x_agreed, aes(YS, Agreed, group = Question)) +
    geom_point(data = x_agreed, aes(YS, Agreed)) +
    scale_colour_manual(values = setNames(c('black','red'),c(T, F))) + 
    geom_text(data = x_agreed, aes(YS, -0.05, label = n), alpha = 0.7)
  p <- p + facet_grid(cols = vars(str_wrap(Question, 25))) +
    scale_y_continuous(labels = scales::percent) +
    labs(title = title, caption = caption) +
    theme(axis.title = element_blank(),
          axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2),
          text = element_text(family = "serif"),
          panel.grid.major.x = element_blank(),
          legend.position = "bottom",
          plot.caption = element_text(hjust = 0))
  p
}
```


MBA
```{r, eval=FALSE}
for(i in 1:length(qidx)){
  title <- paste("Pergrine Exit Survey, MBA,", names(qidx)[i], "Questions")
  this <- qidx[[i]]
  p <- draw_graph(tbl.mba.answer %>% filter(QID %in% this),
                  tbl.mba.agreed %>% filter(QID %in% this), title)
  print(p)
  # ggsave(paste0("fig/", title, ".png"), p, width = 7, height = 7)
}
```

```{r, eval=FALSE}
for(i in 1:length(qidx)){
  title <- paste("Pergrine Exit Survey, BS,", names(qidx)[i], "Questions")
  this <- qidx[[i]]
  p <- draw_graph(tbl.und.answer %>% filter(QID %in% this),
                  tbl.und.agreed %>% filter(QID %in% this), title)
  print(p)
  # ggsave(paste0("fig/", title, ".png"), p, width = 7, height = 7)
}
```

Previous results have been re-created.

Individual Graph
--------------------------------------------------------------------------------
For ACBSP report, I need individual graphs and additional information.

```{r}
# Instead of facet, separate each graph

tbl_und <- tbl.und.answer %>% 
  left_join(tbl.und.agreed,
            by = c("YS", "nYS", "Question", "QID"),
            suffix = c("_answer", "_total"))
tbl_mba <- tbl.mba.answer %>% 
  left_join(tbl.mba.agreed,
            by = c("YS", "nYS", "Question", "QID"),
            suffix = c("_answer", "_total"))
tbl_all <- bind_rows(tbl_und %>% mutate(Degree = "UND"),
                     tbl_mba %>% mutate(Degree = "MBA")) %>% 
  mutate(lnYS = paste0(YS, "\n(n=", n_total, ")"),
         lDegree = str_replace(Degree, "UND", "Undergraduate"))
```


```{r}
draw_bl <- function(qid, deg){
  x <- tbl_all %>% filter(QID == qid, Degree == deg)
  ldeg <- x %>% pull(lDegree)
  ttl <- paste("Survey Result,", ldeg, "Program,", qid)
  subt <- x %>% pull(Question) %>% str_wrap(width = 60)
  ncat <- nlevels(factor(x$YS))
  
  p <- ggplot(x) +
    geom_col(aes(fct_reorder(lnYS, nYS), n_answer, fill = Answer), position = "fill") +
    scale_fill_brewer(palette = "RdYlBu", drop = FALSE,
                      labels = function(x) str_wrap(x, 8)) +
    # annotate("text", x = 1, y = 0.85, label = "Benchmark: 80%",
    #          color = "red", size = 3, alpha = 0.8) +
    annotation_custom(grid::textGrob("80%",
                                     gp = grid::gpar(col = "red",
                                                     fontsize = 6,
                                                     alpha = 0.6)), 
        xmin=0.0, xmax=0.0, ymin=.8, ymax=.8) +
    geom_hline(yintercept = 0.8, color = "red", alpha = 0.5) +
    geom_line(aes(lnYS, Agreed, group = Question)) +
    geom_point(aes(lnYS, Agreed)) +
    scale_colour_manual(values = setNames(c('black','red'),c(T, F)))
  p <- p +
    scale_y_continuous(labels = scales::percent) +
    labs(title = ttl, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    ggthemes::theme_fivethirtyeight(base_size = 7) +
    theme(legend.position = "right",
          legend.direction = "vertical",
          plot.margin = unit(c(1,1,1,2), "lines")) +
    coord_cartesian(xlim = c(0.8, ncat), clip="off")
  p
}

# # Test
# draw_bl("Q16", "UND")
# p <- draw_bl("Q15", "UND")
# ggsave(paste0("fig/test_survey.png"), p,
#        height = 3.5, width = 4.5, units = "in")
```

Save graphics
```{r, eval=FALSE}
dir.create("fig")
dir.create("fig/Survey")
for(d in c("UND", "MBA")){
  for(i in paste0("Q", 15:36)){
    ggsave(paste0("fig/Survey/", d, i, ".png"), draw_bl(i, d),
           height = 3.5, width = 4.5, units = "in")
  }
}
```

Conclusion
================================================================================
Not informative as a note, since graphs are exported for ACBSP reporting.