---
title: "Note to Update External Direct 03"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
datapath <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
```

```{r load}
asm_map <- read_excel(paste0(datapath, "Assessment Data Main.xlsx"), "Mapping")
```

Individual Peregrine to Summary
--------------------------------------------------------------------------------
Import individual data and benchmark scores.
```{r}
fn <- "External Direct Comparison//IndividualResults_UND.xlsx"
tmp1 <- read_excel(paste0(datapath, fn), sheet = 2, skip = 5)
fn <- "External Direct Comparison//IndividualResults_MBA.xlsx"
tmp2 <- read_excel(paste0(datapath, fn), sheet = 2, skip = 5)
tmp3 <- bind_rows(tmp1, tmp2)
names(tmp3)[1] <- "ID"

mdf <- tmp3 %>% select(-(Learner:`Student ID`)) # Remove private information

rm(list = ls(pattern = "tmp?"))
```


```{r}
fn <- "External Direct Comparison//External Direct Comparison.xlsx"
ref <- read_excel(paste0(datapath, fn), "Both")
names(ref) <- c("Course", "Timeline", "Score", "ACBSP_US", "ACBSP_R2", "US",
                "MSCHE", "Public", "Degree")
```

Create variables, reshape data set, and merge benchmark score data.
```{r}
mdf <- mdf %>%
  mutate(
    Time = ymd_hms(Completed),
    AY = case_when(
      Time %within% interval(ymd("2016-06-01"), ymd("2017-05-31")) ~ "2016",
      Time %within% interval(ymd("2017-06-01"), ymd("2018-05-31")) ~ "2017",
      Time %within% interval(ymd("2018-06-01"), ymd("2019-05-31")) ~ "2018",
      Time %within% interval(ymd("2019-06-01"), ymd("2020-05-31")) ~ "2019",
      TRUE ~ "Other"),
    Major = `Identify Your Major or Concentration`,
    Minor = `Identify Your Minor or Certificate`,
    Specialization = `MBA Specialization`,
    Degree = Program)

# Filter entries with less than 30 min spent
mdf.original <- mdf
mdf <- mdf %>% filter(`Duration (min)` > 30)

# Reshape the data
lmdf <- mdf %>% select(-c(Timeline, Faculty, Course)) %>% 
  pivot_longer(cols = c(Accounting:`Final Score`),
               names_to = "Course", values_to = "Score")
# Merge the benchmark scores and compute differences
# Need this at this stage in order to summarize prevelence of achievements
lmdf <- lmdf %>%
  left_join(ref %>% select(Course, ACBSP_US, ACBSP_R2, US, Degree),
            by = c("Degree", "Course")) %>% 
  mutate(Diff = Score - US)

# Name has changed 2019 for *General Business* to *ISBC* (along with the program
# change). Count them together.
lmdf <- lmdf %>%
  mutate(Major = str_replace(Major,"Interdisciplinary Studies in Business and Commerce", "General Business"),
         Degree = str_replace(Degree, "BS", "UND"))

```

Aggregate by different level (all business major, by major, by specialization).
```{r}
# Aggregate: All students
tbl1 <- lmdf %>% group_by(Degree, AY, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>%
  mutate(Major = "All", Specialization = "All")
# Disaggregate: By major
tbl2 <- lmdf %>% filter(Degree == "UND") %>% 
  group_by(AY, Major, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>% 
  mutate(Degree = "UND")
# Disaggregate: By specialization
tbl3 <- lmdf %>% filter(Degree == "MBA") %>% 
  group_by(AY, Specialization, Course) %>% 
  summarise(mean = mean(Score, na.rm = TRUE)/100,
            mean_diff = mean(Diff, na.rm = TRUE)/100,
            met = mean(Diff >0, na.rm = TRUE),
            n = n_distinct(ID)) %>% 
  mutate(Degree = "MBA")
tbl_all <- bind_rows(tbl1, tbl2, tbl3)
# tbl_und <- bind_rows(tbl1 %>% select(-Specialization), tbl2)
# tbl_mba <- bind_rows(tbl2 %>% select(-Major), tbl3)

# Re-introduce benchmark. Use only US.
ref <- ref %>% mutate(Degree = str_replace(Degree, "BS", "UND"))
tbl_all <- tbl_all %>%
  left_join(ref %>% select(Degree, Course, US),
            by = c("Degree", "Course")) %>% 
  mutate(US = US/100)
```


```{r}
dim(tbl_all)
summary(tbl_all)
```


Outcome Table
--------------------------------------------------------------------------------

### Program Level Assessment
Using the mapping, extract relevant information.
```{r}
# Extract relevant rows from the outcome summary
# while adding the identification information
lres <- list()
for(i in c(1:nrow(asm_map))){
  # Selectors
  course <- asm_map[[i, "external_tool"]]
  degree <- asm_map[[i, "degree"]]
  major <- asm_map[[i, "external_group"]]
  control <- asm_map[[i, "external_control_group"]]
  # Identifier
  program <- asm_map[[i, "program"]]
  plo <- asm_map[[i, "plo"]]
  # Populate the list by extracting
  z1 <- tbl_all %>%
    filter(Degree == degree, Major == major, Course == course) %>%
    select(AY, Degree, Major, Course, n, mean, met, US) %>% 
    mutate(Program = program, PLO = plo)
  z2 <- tbl_all %>%
    filter(Degree == degree, Major == control, Course == course) %>%
    select(AY, Degree, Control = Major, n_ctrl = n, mean_ctrl = mean, met_contrl = met)
  lres[[i]] <- left_join(z1, z2, by = c("AY", "Degree"))
}
out_program <- bind_rows(lres) %>% arrange(Program, PLO, Major, AY)
```

### Core Level Assessment
Business Core assessment for each majors. First, result rows relevant. This will contain results for all business majors or MBA and by major/specialization. Then, separate the outcomes by all the business majors or MBA. Finally, 'glue' them to relevant rows (identified by degree and course/topic).

```{r}
# Now use just core objectives
core_map <- asm_map %>% filter(core)
program_map <- asm_map %>% filter(!core)

# Retrieve, edit, and add
# For program level (list)
# Number of programs x Number of Program LOs (each)
# For core level (matrix)
# Number of programs x Number of Core LOs

# Extract data by identifiers: degree, major (who took it), course (topic)

# For each core lo, obtain for all programs
# Input of data, lo, and program... Enough?
# Function to retrieve data manually
# Then function to pull the selectors from the mapping

extract_ext <- function(degree, course, main_group, comp_group, lo, prg){
  tmp1 <- tbl_all %>%
    filter(Degree == degree, Major == main_group, Course == course) %>%
    select(AY, Degree, Course, US,
           main_group = Major, main_n = n, main_mean = mean, main_met = met) %>% 
    mutate(Program = prg, PLO = lo)
  tmp2 <- tbl_all %>%
    filter(Degree == degree, Major == comp_group, Course == course) %>%
    select(AY, Degree, Course,
           comp_group = Major, comp_n = n, comp_mean = mean, comp_met = met)
  left_join(tmp1, tmp2, by = c("AY", "Degree", "Course"))
  
}

# Program map
lres <- mapply(extract_ext, lo = program_map$plo, degree = program_map$degree, course = program_map$external_tool, main_group = program_map$external_group, comp_group = program_map$external_control_group, prg = program_map$program, SIMPLIFY = FALSE)

out <- bind_rows(lres)

write_csv(out, "out/ext-prog-assessment.csv")
```


```{r}
lprograms <- levels(factor(program_map$external_group))

extract_ext_core <- function(prog){
  out_list <- mapply(extract_ext, lo = core_map$plo, degree = core_map$degree, course = core_map$external_tool, main_group = prog, comp_group = core_map$external_control_group, prg = core_map$program, SIMPLIFY = FALSE)
  out_core <- bind_rows(out_list) %>% arrange(Program, PLO, AY)
  out_core
  
}

lres <- sapply(lprograms, extract_ext_core, simplify = FALSE, USE.NAMES = TRUE)
out <- bind_rows(lres)

# What about LO x Target? Simplify to outer(X, Y, FUN = this)?
# LO >> All the argument for extract_ext except for target group?
write_csv(out, "out/ext-core-assessment.csv")
```

