---
title: "Developing Leadership Skills through Assessment"
subtitle: "ACBSP Region 2 Conference"
author:
  - Edmund Matecki^[Associate Professor of Economic, California University]
  - Kentaro Murayama^[Visiting Assisstant Professor of Economics, California University]
date: "November 5-6, 2020"
output:
  powerpoint_presentation:
      reference_doc: my-style01.pptx
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
```

# Motivation: Why do we care about leadership?

- Survey
- Initial assessment

# The Change

```{r}
df <- data.frame(name = c(rep("Old", 2) , rep("New", 2)),
                 type = rep(c("Leadership", "Else"), 2),
                 value = c(23, 77, 40, 60)/100
                 )
ggplot(df) +
  geom_col(aes(x = factor(name, levels=c("Old", "New")), y = value,
               fill = factor(type, levels=c("Else", "Leadership"))),
           position = "stack") +
  scale_fill_manual(values = c("grey", "red")) +
  ggtitle("Leadership Objectives, Now and Then (%)") +
  scale_y_continuous(labels = scales::percent) +
  xlab("") + ylab("") +
  theme_minimal() +
  theme(legend.position = "None", aspect.ratio = 1)
```


# Curriculum Improvements


# Multi-pronged Assessment Regime

Diagram

# Automation of Data Collection & Analysis

Diagram

# Assessing Leadership: Business Core

- LO7: Discern ethical choices and critically evaluate the ethical choices of others.
- LO8: Evaluate socio-cultural and international diversity variables in decision making.
- LO9: Work collaboratively with and provide feedback to others in a team setting.
- LO10: Reflect on personal leadership growth and potential.
  
  
# Demonstration: Business Core LO 8

1. Re-define Learning Objectives
2. Re-design Assessment Tools
3. Implement Standardized Assessment Mechanisms
4. Automate Data Collection and Processing
5. Communicate Feedback

# 1. Re-define Learning Objectives

Learning Objective: Evaluate socio-cultural and international diversity variables in decision making.


# 2. Re-design Assessment Tools

- External Tool: Peregrine CPC Exam
- Internal Tool: Project Assignment "Ethics Case"


# 3. Implement Standardized Assessment Mechanisms

(Sereis of Screenshots)

# 4. Automate Data Collection and Processing

## Challenges

- Inconsistency in rubrics (e.g. word choices, typos, etc.)
- Variations in the data sources (e.g. external/internal, rubric/exam, etc.)
- Timely responses for feedback

## Solutions

- Literal programming for reproducible analysis
- Iterative data processing


# 5. Communicate Feedback

- Annual Department Retreat
  - Assessment outcomes for core objectives
  - Assessment outcomes for each program
  - Strategy development
- 

## Complementary Design in Action

Challenge: Internal and external assessment outcomes are not directly comparable

- Track the changes over time
- Two-dimensional dynamics
- Possible calibration


# Single Measures

Graphs


# Combined Measures

Graph



# Feedback & Strategy Development

## Annual Meeting & Strategy Development

- Data analysis provided
- Discuss the findings with additional qualitative information from discutants
- Review the existing assessment tools in light of learning objectives
- Propose changes in assessment tools (and/or learning objectives)


## Continuous Feedback

- Assessment Committee
- Curriculum Development Committee
- Individual faculty members (both regular and temporary)


