---
title: "Process new data"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---

```{r init}
library(tidyverse)
library(readxl)
rootpath <- "C:\\Users\\HP\\California University of Pennsylvania"
datapath <- paste0(rootpath, "\\ACBSP data reporting - Documents\\Data\\")

path <- paste0(datapath, "Internal Direct Assessment\\")
```


# Introduction

Data import procedures for AY2019 and 2020 are inconsistent and confusing.
In this memo, I would like to explore them and find a way to unify them. As a base framework, I plan to make a set of "raw" data files that can be further processed automatically. Namely, I will have:

- `Survey data` for rubric information such as instructor name, rubric ID, and comments;
- `Rubric outcome data` for outcomes of students' learning assessment drawn from the D2L database; and
- `Master data` for the historical data of students' learning assessment across years.

In order to make the analysis reproducible and traceable, I would like to start from the data as raw as possible. On the one hand, `Rubric outcome data` is suited for correction by scripts because it is produced systematically. On the other hand, `Survey data` are full of human errors and small. A manual pre-processing is beneficial. Lastly, the `Master data` are rarely subject to changes and hence can be used as a reference point for the naming convention and selection.

Therefore, I would like to establish the way to process those data manually or programmatically, depending on the nature of data set, and document such procedures.
In the following, ... (outline later).

(What about other aspects like external direct?)

# Source of Incocistencies

First and most importantly, inconsistencies can be due to the change in D2L versions and/or implementations, columns available to the analysis may change year by year. For instance, between AY2019 and AY2020, there was a major version change in D2L system that involved how the database is structured. The new structure was explored by the analyst and admin, resulting in the new set of columns to be drawn from the database.

Second, naming convention may differ as a result of non-standardized procedures. As mentioned above, some data analyses and preparations are exploratory and unplanned. Moreover, it is iterative with a number of trials and errors. As a result, inconsistent names and definitions are introduced in the process. After the two iterations (AY2020 and AY2021), it is probably time to set a unified framework to impose in the future.

(What type of inconsistencies? Addressing ones in contents as well?)

# Data

All the data for the *internal direct* assessments are stored under `ACBSP data reporting - Documents\Data\Internal Direct Assessment` for now.

## Survey

- `Assessment Survey Responses.xlsx` for AY20. Quite messy. Renames and such in `R/int_munge.R`
- `Rubrics_07302021.xlsx` has a tab `survey` for AY21.
- `SurveyAY21.xlsx` for AY22.

Let's establish the column names:

- ID: Internal ID
- Start: Start time of the survey
- End: End time of the survey
- Email: Email of the person who filled the survey
- Surveyed: Name of the person who filled the survey
- Name: Name of the instructor (usually the same as surveyed)
- Semester: Semester of the course
- Year: Calender year of the course
- AY: Academic year of the course
- Program: 3-letter program ID of the course (e.g., ECO)
- Course: Course ID including the 3-digit numbers (e.g., ECO-201)
- Section: Comprehensive ID for the implementation of the course (e.g., ECO-201-002) 
- Rubric: Indicator variable of whether the assessment is done with rubrics or not
- URL: URL of the rubric if applicable
- AssessmentName: Name of the assessment as specified in the plan
- ObjectiveName: Name of the objective as specified in the plan
- TotalN: Total number of students (NA if rubric is used)
- MetN: Number of students who met the criteria (NA if rubric is used)
- Analysis: Analysis of the outcomes by the surveyed
- Action: Action plan from the analysis by the surveyed

These names can be imposed to the survey file programmatically and/or manually as a one-time procedure. Moreover, some obvious errors in data can be fixed.

For the new survey, this is usually an iterative process. For instance, if a survey entry contains no usable URL, then it needs to be discarded and a new entry is requested.

The end result can be saved as a csv file, avoiding special letters. Name each as `survey_ay#dd.csv`.

AY19 survey:

```{r}
# Not run
fn <- "Assessment Survey Responses.xlsx"
survey <- read_excel(paste0(path, fn), "Edited")
qs <- names(survey)
nms <- c("ID" = "ID",
         "Drop" = "Drop",
         "Start ti" = "Start",
         "Completi" = "Complete", 
         "Email" = "Email",
         "Name" = "Instructor",
         "In which" = "Semester",
         "Course A" = "Course.Section.Original",
         "Course" = "Course",
         "Section" = "Section",
         "What is " = "Assessment.Original",
         "Assessme" = "Assessment",
         "Follow u" = "Follow up",
         "I graded" = "Rubric",
         "Copy and" = "URL",
         "Analysis" = "Analysis.Rubric",
         "Action f" = "Action.Rubric",
         "What is " = "PLO.Original",
         "PLO" = "PLO",
         "What is " = "n.original",
         "n" = "n",
         "If this " = "np.original",
         "np" = "np",
         "Analysis" = "Analysis.Non.Rubric",
         "Action f" = "Action.Non.Rubric")
names(survey) <- nms
id.drop <- c(22, 66, 65, 61, 62, 114, 37, 64, 63)
survey <- survey %>% filter(!ID %in% id.drop)
survey <- survey[!survey$Drop, ]
write_csv(survey, file = paste0(path, "survey_ay19.csv"))
```

AY20 survey:

```{r}
fn <- "Rubrics_07302021.xlsx"
survey <- read_xlsx(paste0(path, fn), "survey")
colnames(survey) <- c("ID", "Exclude", "Start", "Completion", "Email", "Survey Name", "Semester", "Course and Section Original", "Course and Section", "Assessment Name Original", "Assessment Name", "Rubric Grade Original", "Rubric Grade", "URL Original", "URL", "Analysis Rubric", "Action Rubric", "LO", "n", "s", "Analysis Non Rubric", "Action Non Rubric")
survey <- survey %>% mutate(across(c(n, s), as.numeric))
# Split course and section
courses <- str_split(survey$`Course and Section`, "-", simplify = TRUE)
survey <- bind_cols(survey, Course = courses[, 1], Section = courses[, 2])
write_csv(survey, file = paste0(path, "survey_ay20.csv"))
```

AY21 Survey:

```{r}
# Temporary folder
rootdir <- "C://Users/HP/OneDrive - California University of Pennsylvania/Data/AY2021 Backup/"
fns <- list.files(path = rootdir)
fns <- grep("Assessment Survey", fns, value=TRUE)
rawdfs <- lapply(paste0(rootdir, fns), read_excel)
# plandf <- read_excel(paste0(rootdir, "1. Assessment Plan at a Glance Copied.xlsx"))

# Clean data
cleandf <- function(mdf, semester){
  mdf <- mdf %>% select(!starts_with(c("Points", "Feedback")))
  mdf <- mdf %>% select(!c("Total points", "Quiz feedback"))
  # Check for expected column number
  ncol(mdf) == 16
  # If pass, then rename all
  mdfnames <- c("ID", "Time1", "Time2", "Email", "Name", "Program", "Number", "OnlySection", "Rubric", "URL",
                "AssessmentName", "ObjectiveName", "TotalN", "SatisfactoryN", "Analysis", "Action")
  colnames(mdf) <- mdfnames
  mdf <- mdf %>% 
    separate(Name, c("Name1", "Name2")) %>% 
    mutate(Course = paste0(Program, "-", Number),
           Section = paste0(Course, "-", OnlySection),
           NameSection = paste0(Name2, "-", Section))
  mdf$Semester <- semester
  mdf
}

surveys <- list()
surveys[[1]] <- cleandf(rawdfs[[1]], "Fall 2021")
surveys[[2]] <- cleandf(rawdfs[[2]], "Summer 2021")
surveys[[3]] <- cleandf(rawdfs[[3]], "Spring 2022")

# Check URL validity
survey <- bind_rows(surveys)
survey$rubricId <- str_extract_all(survey$URL, "rubricId=[0-9]{6}", simplify=TRUE)
survey$ou <- str_extract_all(survey$URL, "ou=[0-9]{7}", simplify=TRUE)

# # One error (May 20th retrieval)
# survey[41, ]
# survey[41, c("Name2", "Section", "Semester", "rubricId", "ou")]
# survey[39:45, c("Name2", "Section", "Semester", "rubricId", "ou")]
# # Another entry covered.

# # Extract rubric ID... Old code, too much assumption about the order?
# # ToDo: Fix and relfect on the code R/int_read.R
# survey$RubricId <- factor(str_extract_all(survey$rubricId, "[0-9]{6}", simplify=TRUE))
# survey[, c("RubricId", "rubricId")]
# 
# # Request
# x <- as.numeric(levels(survey$RubricId))
# # write.csv(x, file = "rubricid.csv", row.names = FALSE)

# Export the survey for the permanent storage
write.csv(survey, file = paste0(path, "survey_ay21.csv"), row.names = FALSE)
```


## Rubric outcomes

- `Rubrics.xlsx` for AY20.
- `Rubrics_07302021.xlsx` tab `rubrics` for AY21.
- `RubricsAY21.xlsx` for AY22.

Those are highly standardized. Names can be changed to be uniform programmatically. Perhaps it is better to save them as csv file.

## Misc

Irregular inputs include

- Mapping keys to identify the corresponding rubric rows
- MBA comprehensive exam outcomes were used for MBA assessment in AY19 and 20
- Files used for testing (not identified)

I can leave them for now. When the school fully transfers to the new system, I can clean them up.



