---
title: "Assessment Report"
output:
  word_document:
    toc: yes
    reference_docx: template01.docx
date: 8/5/2020
params:
  program: "Business Core"
  code: "BUS"
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
```

Objectives
================================================================================
The goal of this document is to develop our narratives for the observed assessment outcomes.
(e.g. If recent assessment outcomes are falling, what would be the cause(s)? If you see growing disparities between internal and external assessment outcomes, what changes have you observed?)
Please document your discussions and findings by typing them into this Word document.

Data
================================================================================
Internal assessment data are derived from your inputs. Thank you again for your cooperation and contributions.
External assessment data are pulled from Peregrine test results.

PLO and Tools Summary
--------------------------------------------------------------------------------

As reminder, please refer to the following table for the PLO and Assessment Tools used in your program.

```{r load, cache=TRUE}
path <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\WIP\\"
asm <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Sheet0")
asm_map <- read_excel(paste0(path, "Assessment Data Main.xlsx"), "Mapping")

asm <- asm %>%
  mutate(int_delta = internal_outcome - internal_target,
         ext_delta = external_outcome - external_target)
asm <- asm %>% mutate(ay_internal_n = paste0(ay, '\nN = ', internal_n), 
                      ay_external_n = paste0(ay, '\nN = ', external_n))
prg <- params$program
# For comments
non <- readRDS("../out/non.Rds")
survey <- readRDS("../out/survey.Rds")
```
```{r}
asm_map %>% filter(program == prg) %>%
  select(plo, description, ends_with("tool_description")) %>%
  knitr::kable(col.names = c("PLO", "Description",
                             "Internal Tool", "Extrnal Tool"))
```

Comments from Survey
--------------------------------------------------------------------------------

Moreover, the comments you have provided are listed in the following table.
Thank you again for your help!

```{r}
tablecols <- c("PLO", "Course", "Analysis", "Action")
x1 <- non %>% filter(str_detect(PLO, params$code)) %>% select(PLO, Course, ends_with("Non.Rubric"))
x2 <- survey %>% filter(str_detect(PLO, params$code)) %>% select(PLO, Course, ends_with(".Rubric")) %>% arrange(PLO)
names(x1) <- tablecols
names(x2) <- tablecols

if ( (nrow(x1) == 0) & (nrow(x2) == 0) ){
  out <- NULL
} else if (nrow(x1) == 0 ){
  out <- x2 %>% arrange(PLO) 
  knitr::kable(out)
} else if (nrow(x2) == 0 ){
  out <- x1 %>% arrange(PLO) 
  knitr::kable(out)
} else {
  out <- bind_rows(x1, x2) %>% arrange(PLO) 
  knitr::kable(out)
}
```


In the following section, trends in assessment outcomes are summarized first, then a snapshot of the latest assessments (2019-20) is presented.
Please use these data visualizations to develop the narratives of our teaching outcomes and processes, identifying strengths and weaknesses. Any changes in students, instructors, or assessments should be identified.
Moreover, please keep in mind that we will discuss strategic plans next week. The development of such narratives is ultimately intended to aid our decision-making process for the coming academic year and beyond.

Report on `r params$program` Program
================================================================================
```{r time}
combine_deltas <- function(prg, yr = 2019){
  p1 <- draw_delta(prg, yr, "External")
  p2 <- draw_delta(prg, yr, "Internal")
  gridExtra::grid.arrange(p1, p2, ncol = 2)
}

draw_time <- function(lo, ori = c("External", "Internal"),
                      typ = c("Summative", "Formative")){
  ori <- match.arg(ori)
  typ <- match.arg(typ) 
  if (ori == "External"){
    outcome <- "external_outcome"
    target <- "external_target"
    ay <- "ay_external_n"
  } else {
    outcome <- "internal_outcome"
    target <- "internal_target"
    ay <- "ay_internal_n"
  }
  x <- asm %>% filter(plo == lo, type == typ)
  if (all(is.na(x$external_outcome)) |
      all(is.na(x$internal_outcome))){
    return(NULL)}
  p <- ggplot(x, aes_string(ay, outcome)) +
    geom_line(aes(group = 1), na.rm = TRUE) +
    geom_point(na.rm = TRUE) +
    geom_hline(aes_string(yintercept = target),
               alpha = 0.4, color = "red", na.rm = TRUE) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L))
  p
}
combine_time <- function(lo, typ){
  x <- asm_map %>% filter(plo == lo, type == typ)
  title <- paste(lo, typ, "Assessment Outcomes")
  title <- paste0(title,
                  str_sub(paste0("\n(", x %>% pull(description)), 1, 70), "...)" )
  title <- paste0(title,
                  paste0("\n(", x %>% pull(internal_tool)), " & ", x %>% pull(external_tool), ")")
  
  p1 <- draw_time(lo, "External", typ)
  p2 <- draw_time(lo, "Internal", typ)
  if (is.null(p1) & is.null(p2)){
    return(NULL)
  }
  if (is.null(p1)){
    p1 <- ggplot() + theme_void()
  } else{
    p1 <- p1 +
      labs(title = "External") +
      ggthemes::theme_fivethirtyeight(base_size = 9) +
      theme(
        plot.subtitle = element_blank(),
        legend.position = "none")
  }
  if (is.null(p2)){
    p2 <- ggplot() + theme_void()
  } else{
    p2 <- p2 +
      labs(title = "Internal") +
      ggthemes::theme_fivethirtyeight(base_size = 9) +
      theme(
        plot.subtitle = element_blank(),
        legend.position = "none")
  }
  gridExtra::grid.arrange(p1, p2, ncol = 2, top = title)
}
```
```{r corr}
draw_corr <- function(prg, ty = c("Summative", "Formative", "Both")){
  type <- match.arg(ty)
  # Select samples and 
  if (ty == "Both"){
    x <- asm %>% filter(program == prg)
  } else {
    x <- asm %>% filter(program == prg, type == ty)
  }
  if (all(is.na(x$external_outcome)) |
      all(is.na(x$internal_outcome))){
    return(NULL)}
  
  xmin <- min(x$internal_outcome, x$internal_target)
  ymin <- min(x$external_outcome, x$external_target)
  
  title <- paste(prg, type, "External vs Internal")
  subtitle <- "Assessment outcomes are plotted to each other."
  subtitle <- paste0(subtitle, "\nRed point is the 2019 result")
  
  p <- ggplot(x, aes(internal_outcome, external_outcome)) +
    geom_path(linetype = "longdash", na.rm = TRUE) +
    geom_point(aes(color = ay == 2019), na.rm = TRUE) +
    scale_color_manual(values = c("black", "red")) +
    geom_hline(aes(yintercept = external_target), color = "black", alpha = 0.3) +
    geom_vline(aes(xintercept = internal_target), color = "black", alpha = 0.3)
  p <- p +
    facet_wrap(vars(plo))
  p + 
    labs(title = title, subtitle = subtitle) +
    xlab("Internal Assessment Outcomes") +
    ylab("External Assessment Outcomes") +
    scale_x_continuous(breaks = 1:10/10,
                       labels=scales::percent_format(accuracy = 5L)) +
    scale_y_continuous(breaks = 1:10/10,
                       labels=scales::percent_format(accuracy = 5L)) +
    coord_cartesian(xlim = c(xmin - 0.05, 1.01), ylim = c(ymin - 0.05, 1.01)) +
    theme_minimal() +
    theme(legend.position = "none",
          aspect.ratio = 1)
}
# draw_corr("Human Resources Management", "Both")
# draw_corr("Accounting", "Summative")
```
```{r delta}
list_plo <- function(prg){
  asm_map %>% filter(program == prg) %>%
    select(plo, description, ends_with("tool_description")) %>%
    knitr::kable()
}
draw_delta <- function(prg, yr = 2019, ori = c("External", "Internal")){
  type <- match.arg(ori)
  
  if (ori == "External"){
    delta <- "ext_delta"
  } else {
    delta <- "int_delta"
  }
  
  title <- paste(prg, ori, "Deltas for", yr)
  subtitle <- "Differences between target achievements and actual outcomes"
  
  x <- asm %>% filter(program == prg, ay == yr)
  p <- ggplot(x, aes_string("plo", delta)) +
    geom_col(na.rm = TRUE) +
    geom_hline(yintercept = c(-0.2, 0.2), color = "red", alpha = 0.5) +
    geom_hline(yintercept = 0.0, color = "black", alpha = 0.4)
  p +
    labs(title = title, subtitle = subtitle) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L),
                       breaks = -5:5/10) +
    ggthemes::theme_fivethirtyeight(base_size = 8) +
    theme(legend.position = "none")
}
# draw_delta("Business Core", ori = "External")
# draw_delta("Human Resources Management", ori = "Internal")
```


Trend Over Time
--------------------------------------------------------------------------------
```{r, fig.width=7, fig.height=3, results='asis'}
lplo <- asm_map %>% filter(program == prg) %>% pull(plo)
ltyp <- asm_map %>% filter(program == prg) %>% pull(type)
for (i in 1:length(lplo)){
  cat(paste(" \n### ", lplo[i], " \n "))
  combine_time(lplo[i], ltyp[i])
  cat(" \n")
}
```

Associations Between Internal and External Assessments
--------------------------------------------------------------------------------
```{r, fig.width=7, fig.height=7}
draw_corr(prg, "Both")
```

Differences from Targets 2019-20
--------------------------------------------------------------------------------
```{r, fig.width=7, fig.height=4}
combine_deltas(prg)
```
