---
title: "Note 03 for annual reports"
date: "11/27/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, include=FALSE}
# knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
options(dplyr.summarise.inform=FALSE) 
library(readxl)
library(gridExtra)
library(knitr)
library(lubridate)
datapath <- "C:\\Users\\kentr\\California University of Pennsylvania\\ACBSP data reporting - Documents\\Data\\"
```

# Objectives

For the Middle State requirements (*Quality Assurance Report*), we need to have our outcome posted on our school website (https://www.calu.edu/academics/business/learning-outcomes/index.aspx).

In the previous note, I assured that the 2019 data process is done properly with the new orientation of the data base file.
In this note, create visualizations with the new data set.


# Data

```{r load}
# File names and worksheet names
fn <- paste0(datapath, "Assessment Data Main.xlsx")
sns <- c("prg", "core", "mba")
mns <- paste0("map_", sns)

# Load data and mappings into lists
ldf <- sapply(sns, function(x) read_excel(fn, x),
              simplify = FALSE, USE.NAMES = TRUE)
lmp <- sapply(mns, function(x) read_excel(fn, x),
              simplify = FALSE, USE.NAMES = TRUE)
```

Data are stored in three sets: Program, Core, and MBA.

```{r}
names(ldf); names(lmp)
```

They have the same columns for identification (`program`, `plo`, `type`, `source`, `ay`) and outcomes (`n` and `outcome`).
Core and MBA outcomes also have disaggregation by majors/specializations.

```{r}
sapply(ldf, names)
```

# Time Plots

Generic functions are nice, but not necessary for this.
The data are well formatted and little applications outside of them.
Set the format with a function and that's about it.

```{r}
draw_time <- function(sn, i, y1 = "outcome", y2 = NULL){
  # Take a map "map_{sn}" and pick the {i}_th entry
  x <- lmp[[paste("map", sn, sep = "_")]][i, ]
  
  # Use the corresponding data
  y <- ldf[[sn]]
  p <- y %>% filter(plo == x$plo, type == x$type, source == x$source) %>% 
    ggplot(aes_string("ay", y1)) +
    geom_line(na.rm = TRUE, linetype = 1) + geom_point(size = 2, na.rm = TRUE) +
    geom_hline(aes(yintercept = x$target), alpha = 0.4, color = "red") +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L)) 
  
  if(!is.null(y2)){
    p <- p + 
      geom_line(aes_string(y = y2), na.rm = TRUE, linetype = 2) +
      geom_point(aes_string(y = y2), size = 2, na.rm = TRUE)
  }
  
  ttl <- paste(x$plo, x$type, x$source)
  subt <- paste0("Assessment Tool: ", x$tool_description)
  p + labs(title = ttl, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    ggthemes::theme_fivethirtyeight(base_size = 7) +
    theme(legend.position = "right", legend.direction = "vertical")
}

draw_time("prg", 1)
draw_time("prg", 25, y2 = "All")
draw_time("core", 1)
draw_time("core", 1, y2 = "acc")
draw_time("mba", 1)
draw_time("mba", 1, y2 = "ba")

```

- Long format, so that legend can be produced easily?
- Count in note, so that it doesn't take much space?

```{r}
y2 <- "All"
x <- lmp$map_prg[25, ]
y <- ldf$prg %>% filter(plo == x$plo, type == x$type, source == x$source)
z <- pivot_longer(y, cols = c(outcome, All), names_to = "Type", values_to = "outcome")
ggplot(z, aes(ay, outcome, group = Type)) + geom_point() + geom_line(aes(linetype = Type))
```

This is easier... Adjust names? Want something consistent with other data.
Adjustment with the mapping would be needed...

Currently the program mapping has `group1` to indicate the type of data group like "CPC" and then `group2` indicates actual group ("Major" in the case of CPC) like "Accounting".
Yet, the comparison group is indicated by `external_control_group` inconsistently.
Meanwhile, core and mba lack those comparison groups in the mapping. Yet implicitly compare with all the groups present in the data.

```{r}
head(ldf$prg)
head(ldf$core)
head(lmp$map_core)
head(lmp$map_prg)
```

The idea of `group` variable is to use it as an identifier, filtering data in rubric data (internal) or in Peregrine data (external).
I can still use it, while combining it with other identifier.

Use

- group_type
- group_main
- group_comp

for program, and

- group_type
- group_main

for core and mba.

Outcome data sheets can have

- n_main
- outcome_main
- n_comp
- outcome_comp
- etc.

Try:

```{r}
ldf$prg <- ldf$prg %>% rename(main_outcome = outcome, main_n = n, comp_outcome = All, comp_n = n_All)
ldf$core <- ldf$core %>% rename(main_outcome = outcome, main_n = n) %>% rename_with(~ paste0(.x, "_outcome"), acc:mkt)
ldf$mba <- ldf$mba %>% rename(main_outcome = outcome, main_n = n) %>% rename_with(~ paste0(.x, "_outcome"), ba:hm)

lmp$map_prg <- lmp$map_prg %>% rename(group_type = group1, group_main = group2, group_comp = external_control_group)
lmp$map_core <- lmp$map_core %>% rename(group_type = group1, group_main = group2)
lmp$map_mba <- lmp$map_mba %>% rename(group_type = group1, group_main = group2)
```

Work with those names. Later, once moving on to the next notebook, I can update the data file.

Update the previous function accordingly.

```{r}
x <- lmp$map_prg[25, ]
y <- ldf$prg %>% filter(plo == x$plo, type == x$type, source == x$source)
z <- pivot_longer(y, cols = ends_with("outcome"), names_to = "Type", values_to = "Outcome")
ggplot(z, aes(ay, Outcome, group = Type)) + geom_point() + geom_line(aes(linetype = Type))
```


```{r}
x <- lmp$map_core[11, ]
y <- ldf$core %>% filter(plo == x$plo, type == x$type, source == x$source)
select(y, ends_with("outcome"))
z <- pivot_longer(y, cols = ends_with("outcome"), names_to = "Type", values_to = "Outcome")
ggplot(z %>% filter(Type %in% c("main_outcome", "acc_outcome")), aes(ay, Outcome, group = Type)) + geom_point() + geom_line(aes(linetype = Type))
names(y)
y %>% select(plo, type, source, starts_with(c("main", c("acc", "eco"))))
```

```{r}
draw_time <- function(sn, i, y1 = "main", y2 = NULL){
  x <- lmp[[paste("map", sn, sep = "_")]][i, ]
  y <- ldf[[sn]] %>% filter(plo == x$plo, type == x$type, source == x$source)
  if(!is.null(y2)){
    y <- y %>% select(plo, type, source, ay, starts_with(c(y1, y2)))
  }
  z <- pivot_longer(y, cols = ends_with("outcome"),
                    names_to = "Type", values_to = "Outcome")
  
  p <- ggplot(z, aes(ay, Outcome, group = Type)) +
    geom_line(aes(linetype = Type), na.rm = TRUE) +
    geom_point(size = 2, na.rm = TRUE) +
    scale_y_continuous(labels=scales::percent_format(accuracy = 5L)) 
  # Using the map (x), add the target level
  p <- p + geom_hline(aes(yintercept = x$target), alpha = 0.4, color = "red")
  
  ttl <- paste(x$plo, x$type, x$source)
  subt <- paste0("Assessment Tool: ", x$tool_description)
  p + labs(title = ttl, subtitle = subt) +
    xlab("Academic Year\nSample Size") +
    ggthemes::theme_fivethirtyeight(base_size = 7) +
    theme(legend.position = "right", legend.direction = "vertical")
}

draw_time("prg", 1)
draw_time("prg", 25, y2 = "comp")
draw_time("core", 1)
draw_time("core", 1, y2 = "acc")
draw_time("core", 1, y2 = c("acc", "eco"))
draw_time("mba", 1)
draw_time("mba", 1, y2 = "ba")
```

Okay, sufficient flexibility.

# Other Plots

## Core Across Groups

```{r}
x <- ldf$core %>% select(program:ay, ends_with("outcome")) %>% filter(plo == "BUS 1", source == "External") %>% pivot_longer(cols = ends_with("outcome"))

ggplot(x %>% mutate(name = str_remove(name, "_outcome")), aes(name, value)) + geom_col() + facet_wrap(vars(ay))
```

```{r}
x <- ldf$core %>% select(program:ay, ends_with("outcome")) %>% filter(source == "External") %>% pivot_longer(cols = ends_with("outcome"))
x <- x %>% mutate(name = str_remove(name, "_outcome"), plo = str_remove(plo, "BUS "))
x
ggplot(x %>% filter(ay == 2019), aes(plo, value - 0.7)) + geom_col() + facet_wrap(vars(name))
ggplot(x %>% filter(ay == 2018), aes(plo, value - 0.7)) + geom_col() + facet_wrap(vars(name))
```


```{r}
x <- ldf$core %>% select(program:ay, ends_with("outcome")) %>% filter(source == "Internal") %>% pivot_longer(cols = ends_with("outcome"))
x <- x %>% mutate(name = str_remove(name, "_outcome"), plo = str_remove(plo, "BUS "))

ggplot(x %>% filter(ay == 2019), aes(plo, value - 0.7)) + geom_col() + facet_wrap(vars(name))
```

